
#load the skeletonized data
```{r message=FALSE, include=FALSE}

target_folder <- "/media/fpreuss/raid5/timelapses/analysis/200703/data/posture/skeletonized_filtered"

#list of .rds files in data folder
files_to_process <- list.files(target_folder, "skeletonized_filtered.rds", full.names = TRUE, ignore.case = TRUE)
selected_annotation <-  c("N2_1:10_OP50_skel")
files_to_process <- grep(selected_annotation,files_to_process,value = TRUE)

#select which timepoint (hours_rounded)
selected_timepoint <- 1:10

data <- files_to_process %>%
    map_df(.,function(x) readRDS(x)) %>%
    #estimate 15 minutes as lag before experiment
    mutate(minutes = 15 + ((tp-1)*8+(tp-1)*0)) %>%
    #round to half hour steps
    # mutate(hours_rounded = ceiling(minutes/60*2)/2) %>%
    #round to full hours steps
    mutate(hours_rounded = ceiling(minutes/60)) %>%
    filter(hours_rounded %in% selected_timepoint) %>%
    mutate(ID = paste0(dataset_ID,"_", tp,"_",TrackID))

```



#select experiment type, dataset and timepoints to process
#we also set a minimum track length ("minimal_track_length" variable) and select a fixed number of random tracks (defined by "numbers_of_displayed_tracls" variable)
```{r message=FALSE, include=FALSE}

sample_ID = sample(1:100,1)

save_path <- "/media/fpreuss/raid5/timelapses/analysis/200703/plots/motion_videos"
save_path_video <- file.path("/media/fpreuss/raid5/timelapses/analysis/200703/plots/motion_videos",paste0(sample_ID, "_",selected_annotation,"_timepoint_",min(selected_timepoint),"-",max(selected_timepoint),"_hours_frames"))
dir.create(save_path_video)

#what is the conversion factor ? how many µm equals one pixel
conversion_factor <- 6.25

#only tracks longer than 30 sec (if 2fps)
minimal_track_length <- 120
#How many tracks are shown?
numbers_of_displayed_tracks <- 300

#calculate track angle and velocity for the selected data
angle_and_velocity <- data %>%
  #summarise by frame and keep location
  group_by(ID,frame,location_x,location_y) %>%
  summarise() %>%
  #now calculate for the whole track (== ID)
  group_by(ID) %>%
  #the track should not have any missing frames
  mutate(length_track = n(), length_track2=last(frame)-first(frame)+1) %>%
  filter(length_track == length_track2) %>%
  #filter out tracks that are too short
  filter(length_track > minimal_track_length) %>%
  select(-c(length_track2)) %>%
  #calculate velocity, angular velocity and center the track position
  mutate(x_lag=lag(location_x,n=1) - location_x, y_lag = lag(location_y, n=1) - location_y) %>%
  mutate(x_lead=lead(location_x, n=1) - location_x, y_lead=lead(location_y, n=1) - location_y) %>%
  # calculate the angle and convert to degrees
  mutate(angle_track = suppressWarnings(180 - (as.numeric(mapply(angle,x_lag,y_lag,x_lead,y_lead)))*180/pi)) %>%
  # measure distance between current point and 1 second before
  mutate(local_distance=suppressWarnings(as.numeric(mapply(distance,lag(location_x,n=2),lag(location_y,n=2),location_x,location_y)))) %>%
  #this will result in velocity based on local distance (µm/s)
  mutate(velocity = local_distance*conversion_factor/2) %>%
  mutate(first_location_x = first(location_x),first_location_y = first(location_y)) %>%
  mutate(location_x_centered = location_x-first_location_x, location_y_centered = location_y-first_location_y) %>%
  ungroup()

#select random tracks
selected_tracks <- angle_and_velocity %>%
  group_by(ID) %>%
  summarise() %>%
  sample_n(numbers_of_displayed_tracks) %>%
  pull()
  
data_for_plotting_sub <- data %>%
  #first filter out only the tracks that have been randomly selected (after filtering)
  filter(ID %in% selected_tracks) %>%
  #to those tracks append the above calculated velocity, angular velocity etc
  left_join(angle_and_velocity,by=c("ID","frame","location_x","location_y"))
 
```


```{r message=FALSE, include=FALSE}
#plot the sampled tracks at their original location
ggplot(data_for_plotting_sub)+
    geom_path(aes(x=location_x, y=location_y,group=ID,color=ID))+
    theme(aspect.ratio = 1024/1024)+
    scale_x_continuous(expand = c(0, 0), limits= c(0,1023))+
    scale_y_continuous(expand = c(0, 0),trans="reverse", limits= c(1023,0))+
    theme_void()+
    theme(legend.position = "none")+
    theme(legend.text = element_text(colour="white", size = 16, face = "bold"))+
    theme(legend.title = element_text(colour="white", size = 16, face = "bold"))+
    ggsave(file.path(save_path,paste0(sample_ID,"_",selected_annotation,"_","timepoints_",min(selected_timepoint),"-",max(selected_timepoint),"_all_tracks",".png")),height = 30,width= 30,units = "cm",bg="black",dpi=150)

#plot the sampled tracks at their centered location
ggplot(data_for_plotting_sub)+
    geom_path(aes(x=location_x_centered, y=location_y_centered,group=ID,color=ID))+
    theme(aspect.ratio = 1024/1024)+
    scale_x_continuous(limits= c(-1023,1023))+
    scale_y_continuous(limits= c(-1023,1023))+
    theme_void()+
    theme(legend.position = "none")+
    ggsave(file.path(save_path,paste0(sample_ID,"_",selected_annotation,"_","timepoint_",min(selected_timepoint),"-",max(selected_timepoint),"_all_tracks_centered",".png")),height = 30,width= 30,units = "cm",bg="black",dpi=150)


```



#plot all skeletons as an overview grid
```{r message=FALSE, include=FALSE}


data_for_plotting_temp <- data_for_plotting_sub %>%
  group_by(ID) %>%
  mutate(frame_norm = frame - min(frame))

frames <- sort(unique(data_for_plotting_temp$frame_norm))
frames <- 1:150


for (selected_frame in frames){
  
  ggplot(data_for_plotting_temp)+
    #manually define area for each skeleton, otherwise there will be slight translation of the whole grid in between frames
    scale_x_continuous(limits = c(-10, 70))+
    scale_y_continuous(expand = c(0, 0),limits=c(70,-10), trans="reverse")+
    geom_point(data=filter(data_for_plotting_temp,frame_norm==selected_frame),aes(X,Y,color=angle),size=0.5)+
    geom_point(data=filter(data_for_plotting_temp,frame_norm==selected_frame & is_head== "YES"),aes(X,Y),color="orange",size=2,shape=17)+
    scale_color_gradient2(low = "deepskyblue", mid = "lavender",
                          high = "deeppink",midpoint=0,limits =c(-1,1),na.value="grey")+
    theme_void()+
    coord_fixed(ratio = 1)+
    theme(legend.position = "none",
          strip.text.x = element_blank())+
    facet_wrap(vars(ID))+
    ggsave(file.path(save_path_video,paste0(sample_ID,"_",selected_annotation,"_","timepoints_",min(selected_timepoint),"-",max(selected_timepoint),"_frame_",selected_frame,".png")),height = 30,width= 30,units = "cm",dpi=200)

}


```



#plot all frames with skeletons in their original location
```{r message=FALSE, include=FALSE}

frames <- sort(unique(data_for_plotting_sub$frame))
for (selected_frame in frames){
  
  data_for_plotting_temp <- data_for_plotting_sub %>%
    filter(frame == selected_frame)
  
  ggplot(data_for_plotting_temp)+
    theme(aspect.ratio = 1024/1024)+
    coord_cartesian(ylim=c(0, 1023))+
    scale_x_continuous(expand = c(0, 0), limits= c(0,1023))+
    scale_y_continuous(expand = c(0, 0),trans="reverse", limits= c(1023,0))+
    geom_point(data=filter(data_for_plotting_temp,frame==selected_frame),aes(location_x+X,location_y+Y,color=angle),size=0.5)+
    geom_point(data=filter(data_for_plotting_temp,frame==selected_frame & is_head== "YES"),aes(location_x+X,location_y+Y),color="orange",size=4,shape=17)+
    scale_color_gradient2(low = "deepskyblue", mid = "lavender",
                          high = "deeppink",midpoint=0,limits =c(-1,1),na.value="grey")+
    theme_void()+
    theme(legend.position = "none")+
    ggsave(file.path(save_path_video,paste0(sample_ID,"_",selected_annotation,"_","timepoints_",min(selected_timepoint),"-",max(selected_timepoint),"_frame_",selected_frame,".png")),height = 30,width= 30,units = "cm",bg="black",dpi=150)
}

```


#plot all frames with skeletons in their centered location
```{r message=FALSE, include=FALSE}

frames <- sort(unique(data_for_plotting_sub$frame))
for (selected_frame in frames){
  ggplot(data_for_plotting_sub)+
    theme(aspect.ratio = 1024/1024)+
    scale_x_continuous(limits= c(-1024/2,1024/2))+
    scale_y_continuous(limits= c(-1024/2,1024/2))+
    geom_point(data=filter(data_for_plotting_sub,frame==selected_frame),aes(location_x_centered+X,location_y_centered+Y,color=angle),size=0.5)+
    geom_point(data=filter(data_for_plotting_sub,frame==selected_frame & is_head== "YES"),aes(location_x_centered+X,location_y_centered+Y),color="orange",size=4,shape=17)+
    scale_color_gradient2(low = "deepskyblue", mid = "lavender",
                          high = "deeppink",midpoint=0,limits =c(-1,1),na.value="grey")+
    theme_void()+
    theme(legend.position = "none")+
    ggsave(file.path(save_path_video,paste0(sample_ID,"_",selected_annotation,"_","timepoints_",min(selected_timepoint),"-",max(selected_timepoint),"_frame_",selected_frame,"_centered.png")),height = 30,width= 30,units = "cm",bg="black",dpi=150)
}
  
```
