
  
#Define locations and datasets to include
```{r, echo=FALSE}
#define save path
save_path <- file.path("/Users/fpreuss/Desktop/data/plots/", "motion")
dir.create(save_path)
```

#Input: Data from "plots_motion_analysis_scatter.Rmd"
#Please excecute this first!
```{r, echo=TRUE}
  
#define colors
library(wesanderson)
#pixel to µm
conversion_factor <- 6.25
#fps we downsampled to (in KNIME)
downsampled_to = 2

#lower velocity limit for mode == roaming (mm/s)
velocity_r <- 0.01
#upper angle limit for mode == roaming (mm/s)
angle_r <-15
# upper velocity limit for mode == still (mm/s)
velocity_s <- 0.001
  
data_binarized <- data %>%
  mutate(mode = ifelse(p_mean_velocity > velocity_r & p_mean_angle < angle_r,"roaming","dwelling")) %>%
  mutate(mode=ifelse(p_mean_velocity < velocity_s, "still", mode)) %>%
  group_by(dataset_ID, tp, TrackID, binning) %>%
  #if there is at least one omega turn in a bin, make it 1 otherwise 0
  mutate(omega = ifelse(p_omega_rf > 0, 1, 0))

#here we will summarise by tp (==video timestep)
#so later in the plots one dot = one (in our case 8 mins long) video 
data_bs <- data_binarized %>%
  group_by(annotation,hours_rounded,tp,mode,dataset_ID) %>%
  #summarise over tp
  #this will be the mean of the bins contained within that tp and mode
  #counts is the number of bins of a certain mode
  #mean_omega is the number of bins with at least one detected omega turn divided by the total number of bins
  summarise(counts=n(),mean_velocity = mean(p_mean_velocity), mean_angle = mean(p_mean_angle),perc_omega = sum(omega)/n()) %>%
  group_by(annotation,hours_rounded,tp,dataset_ID) %>%
  #total counts
  mutate(sum=sum(counts)) %>%
  #relative occurence of mode
  mutate(perc = counts/sum) %>%
  ungroup()
  
# here we will summarise per track
# so later in the plots one dot = one track
data_bst <- data_binarized %>%
  group_by(annotation,hours_rounded,tp,TrackID,dataset_ID,mode,binning,omega) %>%
  #summarise over individual tracks
  #this will be the mean of the bins contained within that track
  #mean_omega is the mean number of tracks with at one omega turn, normalized per s
  summarise(mean_velocity = mean(p_mean_velocity), mean_angle = mean(p_mean_angle))

unique(data$annotation)

```
#function for plotting mean mode fraction with Local Polynomial Regression Fitting
```{r, echo=TRUE}


se <- function(x) sqrt(var(x)/length(x))

plot_mean_w_error <- function(data_to_plot, X, Y,colored_by){
  ggplot(data_to_plot,aes_string(x = X ,y =Y,color=colored_by,fill=colored_by,group=colored_by)) +
    geom_ribbon(aes_string(ymin="minse", ymax="maxse",group=colored_by),fill="lightgray", color="lightgray", alpha=.8)+
    geom_line(size=1.2)+
    geom_point(shape=21,size=2.5,color="black")+
    scale_x_continuous(breaks=(seq(1,show_until)))+
    theme_bw()+
    labs(x="time (hours)", "relative fraction")+
    theme(strip.background = element_rect(colour = "white", fill = "white"),
      strip.text.x = element_text(size=20,colour = "black", face = "bold"),
      axis.text.x = element_text(size=15, face="bold"),
      axis.title.x = element_text(size=20, face="bold"),
      axis.text.y = element_text(size=15, face="bold"),
      axis.title.y = element_text(size=20, face="bold"),
      axis.line = element_line(colour = 'black', size = 1.2),
      axis.ticks = element_line(colour = "black", size = 1.2))+
    scale_fill_manual(values = pal)+
    scale_color_manual(values = pal)
}


#function for plotting boxplots
plot_boxplots <- function(data,X,Y,fill_by){

  ggplot(data,aes_string(x=X,y=Y,fill=fill_by))+
    # geom_point(size=0.75,alpha=0.25,shape=21,position=position_jitterdodge(0.25))+
    geom_boxplot(alpha=1,outlier.size=0.5)+
    theme_classic()+
    scale_fill_manual(values=pal)+
    theme(
      legend.direction="horizontal",
      legend.position = "top",
      strip.background = element_rect(colour = "white", fill = "white"),
      panel.spacing = unit(1, "lines"),
      strip.text.x = element_text(size=15,colour = "black", face = "bold"),
      axis.text.x = element_text(size=10),
      axis.title.x = element_text(size=20),
      axis.text.y = element_text(size=20),
      axis.title.y = element_text(size=20),
      axis.ticks=element_line(size=1.5),
      axis.ticks.length=unit(0.25,"cm"),
      axis.line = element_line(colour = 'black', size = 1.5))

}

#function for plotting point plots with range
plot_dots <- function(data_bs,Y,ylab,fill_by){
  
  
  ggplot(data_bs,aes_string(x="annotation",y=Y,fill=fill_by))+
    #
    {
      if(length(selected_annotations) > 2)
    geom_violin(fill="grey", alpha=0.25,lwd=0)
    } +
    # geom_point(alpha=0.25,size=2,shape=21,position = position_jitterdodge(jitter.width = 0.6))+
    geom_boxplot(alpha=0.5,outlier.shape = 21)+
    labs(y=paste0(Y, " (", selected_mode,")"))+
    theme_classic()+
    scale_fill_manual(values=pal)+
    theme(
      legend.direction="horizontal",
      legend.position = "top",
      strip.background = element_rect(colour = "white", fill = "white"),
      panel.spacing = unit(1, "lines"),
      strip.text.x = element_text(size=15,colour = "black", face = "bold"),
      axis.text.x = element_text(size=10),
      axis.title.x = element_text(size=20),
      axis.text.y = element_text(size=20),
      axis.title.y = element_text(size=20),
      axis.ticks=element_line(size=1.5),
      axis.ticks.length=unit(0.25,"cm"),
      axis.line = element_line(colour = 'black', size = 1.5))
  
}

plot_omega <- function(data_bs, selected_mode, selected_annotations){
  data_bsf <<- data_bs %>%
    filter(annotation %in% selected_annotations) %>%
    filter(hours_rounded %in% selected_hours) %>%
    filter(mode %in% selected_mode) %>%
    mutate(annotation = factor(annotation, levels = selected_annotations)) %>%
    arrange(annotation) 
  
  data_bsfs <- data_bsf %>%
    group_by(annotation,hours_rounded) %>%
    summarise(
      sd = sd(perc_omega, na.rm=TRUE),
      # sem = se(perc),
      perc_omega = median(perc_omega)
    )
  
  ggplot(data_bsf,aes(x=time,y=perc_omega,fill=annotation))+
        geom_boxplot(lwd=1.2,outlier.shape = NA)+
        geom_point(position = position_jitterdodge(jitter.width=0.25),color="black",shape=21,size=2.5,alpha=0.5)+
        # geom_pointrange(data = data_bsfs,aes(ymin = perc_omega-sd, ymax = perc_omega+sd),color="black",position = position_dodge(0.75))+
        scale_fill_manual(values=pal)+
        xlab("hours") + ylab(paste0("fraction omega turns"))+
        theme_classic()+
        theme(
          legend.direction="horizontal",
          legend.position = "top",
          strip.background = element_rect(colour = "white", fill = "white"),
          panel.spacing = unit(1, "lines"),
          strip.text.x = element_text(size=15,colour = "black", face = "bold"),
          axis.text.x = element_text(size=30),
          axis.title.x = element_text(size=20),
          axis.text.y = element_text(size=30),
          axis.title.y = element_text(size=20),
          axis.ticks=element_line(size=1.5),
          axis.ticks.length=unit(0.25,"cm"),
          axis.line = element_line(colour = 'black', size = 1.5))
}

```


#plot modes
```{r, echo=TRUE}
save_path_temp <- file.path(save_path,"modes")
dir.create(save_path_temp)



selected_annotations <- c("Agar","OP50_with_Az_NGM","OP50")
selected_mode <- c("roaming")
pal <- wes_palette("Darjeeling1")[c(1,2,5)]
data_bs %>%
  filter(annotation %in% selected_annotations) %>%
  arrange(match(annotation, selected_annotations)) %>%
  mutate(annotation=factor(annotation, levels=selected_annotations)) %>%
  group_by(hours_rounded,annotation,mode) %>%
  summarise(mean_perc= mean(perc), maxse=mean(perc)+sd(perc),minse=mean(perc)-sd(perc)) %>%
  filter(mode %in% selected_mode) %>%
  plot_mean_w_error(., "hours_rounded", "mean_perc","annotation") +
    facet_wrap(vars(annotation),ncol=1)+
    scale_y_continuous(limits=c(0,NA))+
    ggsave(file.path(save_path_temp,paste0("modes_relative_per_mode_seperate_sd.png")),height=7,width=5,dpi=600)


#Baris data
selected_annotations <- c("OP50","BAT2206","BAT2198")
selected_mode <- c("roaming")
pal <- rep("black",length(selected_annotations))
data_bs %>%
  filter(annotation %in% selected_annotations) %>%
  arrange(match(annotation, selected_annotations)) %>%
  mutate(annotation=factor(annotation, levels=selected_annotations)) %>%
  group_by(hours_rounded,annotation,mode) %>%
  summarise(mean_perc= mean(perc), maxse=mean(perc)+se(perc),minse=mean(perc)-se(perc)) %>%
  filter(mode %in% selected_mode) %>%
  plot_mean_w_error(., "hours_rounded", "mean_perc","annotation") +
    facet_wrap(vars(annotation),ncol=3)+
    scale_y_continuous(limits=c(0,NA))+
    ggsave(file.path(save_path_temp,paste0("BARIS_modes_relative_per_mode_seperate.png")),height=5,width=10,dpi=600)


```

#plot relative occurence of dwelling AND roaming for all timepoints for all conditions -- BOXPLOT
```{r, echo=TRUE}
save_path_temp <- file.path(save_path,"modes_boxplots")
dir.create(save_path_temp)

selected_annotations <- c("Agar","OP50_with_Az_NGM","OP50","OP50_after_6h_exit")
selected_mode <- c("dwelling")

pal <- wes_palette("Darjeeling1")[c(1,2,5,4)]
data_bs %>%
  filter(annotation %in% selected_annotations) %>%
  arrange(match(annotation, selected_annotations)) %>%
  mutate(annotation=factor(annotation, levels=selected_annotations)) %>%
  mutate(hours_rounded = as.factor(hours_rounded)) %>%
  group_by(hours_rounded,annotation,mode) %>%
  filter(mode %in% selected_mode) %>%
  ungroup() %>%
  plot_boxplots(., "hours_rounded","perc","annotation") +
    facet_wrap(vars(mode),ncol=1,scales="free_x")+
    ggsave(file.path(save_path_temp,paste0("modes_relative_box_",a,".png")),height=5,width=5,dpi=600)
  

  
```

#plot distributions
```{r, echo=TRUE}
save_path_temp <- file.path(save_path,"velocity")
dir.create(save_path_temp)

selected_annotations <- c("Agar","OP50")

pal <- wes_palette("Darjeeling1")[c(1,5)]
data %>%
  filter(annotation %in% selected_annotations) %>%
  arrange(match(annotation, selected_annotations)) %>%
  mutate(annotation=factor(annotation, levels=selected_annotations)) %>%
  mutate(time = ifelse(hours_rounded <= 4, "1",NA)) %>%
  mutate(time = ifelse(hours_rounded > 4 & hours_rounded <= 8, "4",time)) %>%
  mutate(time = ifelse(hours_rounded > 8 & hours_rounded <= 12, "8",time)) %>%
  ggplot(., aes(x= p_mean_velocity,fill=annotation))+
    geom_density(alpha=0.5)+
    theme_classic()+
    facet_wrap(vars(time,annotation),ncol=2,scales="free_y")+
    scale_fill_manual(values = pal)+
    scale_color_manual(values = pal)+
    ggsave(file.path(save_path_temp,paste0("velocity_density_",paste(selected_annotations, collapse = "_"),".png")),height=3,width=5,dpi=600)

###
save_path_temp <- file.path(save_path,"angular_velocity")
dir.create(save_path_temp)

selected_annotations <- c("Agar","OP50")

pal <- wes_palette("Darjeeling1")[c(1,5)]
data %>%
  filter(annotation %in% selected_annotations) %>%
  arrange(match(annotation, selected_annotations)) %>%
  mutate(annotation=factor(annotation, levels=selected_annotations)) %>%
  mutate(time = ifelse(hours_rounded <= 4, "1",NA)) %>%
  mutate(time = ifelse(hours_rounded > 4 & hours_rounded <= 8, "4",time)) %>%
  mutate(time = ifelse(hours_rounded > 8 & hours_rounded <= 12, "8",time)) %>%
  ggplot(., aes(x= p_mean_angle,fill=annotation))+
    geom_density(alpha=0.5)+
    theme_classic()+
    facet_wrap(vars(time,annotation),ncol=2,scales="free_y")+
    scale_fill_manual(values = pal)+
    scale_color_manual(values = pal)+
    ggsave(file.path(save_path_temp,paste0("velocity_density_",paste(selected_annotations, collapse = "_"),".png")),height=5,width=7,dpi=600)



```

#plot velocity comparisons for specific timepoints and conditions
```{r, echo=TRUE}


library(ggsignif)
#for Dunnett's test
library(multcomp)
#for exporting Dunnett's test result
library(broom)

#boxplots
pal <- wes_palette("Darjeeling1")[c(5,4,1,2)]
selected_mode <- c("still","dwelling")
selected_parameter <- "mean_angle"
selected_annotations <- c("OP50","daf2","OP50_after_6h_exit")


save_path_temp <- file.path(save_path,selected_parameter)
dir.create(save_path_temp)

data_bsf <- data_bs %>%
  mutate(time = ifelse(hours_rounded <= 2, "1",NA)) %>%
  # mutate(time = ifelse(hours_rounded > 2 & hours_rounded <= 8, "2",time)) %>%
  mutate(time = ifelse(hours_rounded > 8 & hours_rounded <= 12, "8",time)) %>%
  na.omit()%>%
  filter(annotation %in% selected_annotations) %>%
  filter(mode %in% selected_mode) %>%
  mutate(annotation =  factor(annotation, levels = selected_annotations)) %>%
  arrange(match(annotation, selected_annotations)) %>%
  mutate(annotation=factor(annotation, levels=selected_annotations))


data_bsf %>%
  plot_dots(., selected_parameter, "velocity (mm/s)","annotation")+
    facet_wrap(vars(time))+
    ggsave(file.path(save_path_temp,paste0(paste(selected_mode,collapse = "_"),"_",selected_parameter,"_",paste(selected_annotations, collapse="_"),".png")),height=5,width=5)

#right order (so that OP50 is first factor and treated as "control" for Dunnett's post-hoc test)
data_bsf$annotation <- relevel(data_bsf$annotation, ref = "OP50")
# Compute the analysis of variance
aov <- aov(eval(as.name(selected_parameter) ~ annotation, data = data_bsf)
# Summary of the analysis
summary(aov)
# Dunnett's post-hoc test
post_test <- glht(aov,
  linfct = mcp(annotation = "Dunnett")
)
write.table(tidy(post_test) %>%
              mutate(test = "Anova with Dunnett Post Hoc test") ,file=file.path(save_path_temp,paste0(paste(selected_mode,collapse = "_"),"_mean_velocity","_",paste(selected_annotations, collapse="_"),".txt")))



```




#compare omega turn occurences across conditions
```{r, echo=TRUE}

save_path_temp <- file.path(save_path,"omega_turns")
dir.create(save_path_temp)

selected_annotations <- c("Agar","OP50_with_Az_NGM","OP50")
selected_mode <- c("roaming")
selected_hours <- c(1:2,10:12)
pal <- wes_palette("Darjeeling1")[c(1,2,5)]

data_bs %>%
  filter(hours_rounded %in% selected_hours) %>%
  mutate(time=ifelse(hours_rounded <= 2,"early",NA)) %>%
  mutate(time=ifelse(hours_rounded >= 10, "late",time)) %>%
  plot_omega(., selected_mode, selected_annotations)+
    ggsave(file.path(save_path_temp,paste0("omega_median",paste(selected_annotations, collapse="_"),"_",paste(selected_hours, collapse="_"),".png")),height=5,width=5,dpi=600)


selected_hours <- seq(1:12)

data_bs %>%
  filter(hours_rounded %in% selected_hours) %>%
  mutate(time=as.factor(hours_rounded)) %>%
  plot_omega(., selected_mode, selected_annotations)+
    ggsave(file.path(save_path_temp,paste0("omega_median",paste(selected_annotations, collapse="_"),"_",paste(selected_hours, collapse="_"),".png")),height=5,width=12,dpi=600)


```





# data_bsf is created by the plot_omega function
# create separate dataframe for each timepoint (if two timepoints have been selected)
data_bsf1 <- filter(data_bsf, hours_rounded == selected_hours[1])
data_bsf2 <- filter(data_bsf, hours_rounded == selected_hours[2])

# for every dataframe (i.e. timepoint) compute separate kruskal wallis test
kw1 <- kruskal.test(perc_omega ~ annotation, data = data_bsf1)
kw2 <- kruskal.test(perc_omega ~ annotation, data = data_bsf2)

#select p-value correction for pairwise wilcox test
padjust <- "BH"

#for each timepoint new dataframe with results from pairwise wilcox test and kruskal wallis p value 
post_test1 <- pairwise.wilcox.test(data_bsf1$perc_omega, data_bsf1$annotation,
                 p.adjust.method = padjust) %>%
  tidy() %>%
  mutate(kw_pvalue = kw1$p.value) %>%
  rename(wilcox_pvalue = p.value) %>%
  mutate(selected_hour = selected_hours[1])

post_test2 <- pairwise.wilcox.test(data_bsf2$perc_omega, data_bsf2$annotation,
                 p.adjust.method = padjust) %>%
  tidy() %>%
  mutate(kw_pvalue = kw2$p.value) %>%
  rename(wilcox_pvalue = p.value) %>%
  mutate(selected_hour = selected_hours[2])

#combine the results of the two wilcox tests and attach methods description
post_test <- rbind(post_test1, post_test2) %>%
  mutate(test = "kruskal-wallis", padjust_method = padjust)

write.table(post_test,file=file.path(save_path_temp,paste0("omega_",paste(selected_annotations, collapse="_"),".txt")))


```

#compare traveled distance across timepoints
```{r, echo=TRUE}

save_path_temp <- file.path(save_path,"traveled_distance")
dir.create(save_path_temp)

selected_annotations <- c("OP50")
selected_hours <- c(1,12)
pal <- wes_palette("Darjeeling1")[c(5)]
selected_mode <- c("dwelling","still")

data_binarized %>%
  filter(annotation %in% selected_annotations) %>%
  filter(mode %in% selected_mode) %>%
  filter(hours_rounded %in% selected_hours) %>%
  mutate(time = as.character(hours_rounded)) %>%
  plot_boxplots(., "distance_per_track", "velocity (mm/s)", "time")+
    geom_signif(comparisons = list(c(as.character(selected_hours[1]), as.character(selected_hours[2]))),map_signif_level = TRUE, textsize=1,test = "wilcox.test")+
    ggsave(file.path(save_path_temp,paste0(paste(selected_mode,collapse="_"),"_traveled_distance","_",paste(selected_annotations, collapse="_"),".png")),height=5,width=5)



 

```
