  
#Define locations
#Also define timerange to be plotted
```{r, echo=FALSE}

#define base path  
base_path <- "/media/fpreuss/raid5/timelapses/analysis/200703"

#Until how many hours
show_until <- 12

```

#load data
```{r, echo=FALSE}

target_path <- file.path(base_path,"data","motion")

#list of centroid tracking .rds files in data folder
files_to_process <- list.files(target_path, paste0("centroid_tracking_"),full.names = TRUE, ignore.case = TRUE)
  
data <- map_dfr(files_to_process,readRDS) %>%
    mutate(hours = minutes / 60) %>%
    #round per half an hour
    # mutate(hours_rounded= floor(hours * 2) / 2) %>%
    #round per hour
    mutate(hours_rounded = ceiling(hours)) %>%
    #filter out first 30 mins
    filter(hours > 0.5) %>%
    #take out one condition
    filter(!annotation %in% c("Agar with NAD",
                              "NGM RT",
                              "NGM",
                              "DA465",
                              "OP50 after 6h exit",
                              "NGM after 6h exit",
                              "OP50 with Az Agar"
                              )) %>%
    na.omit() %>%
    # scale velocity to mm/s
    mutate(p_mean_velocity = p_mean_velocity / 1000) %>%
    group_by(annotation, hours_rounded) %>%
    filter(hours_rounded <= show_until) %>%
    #count tracks per hour per condition
    mutate(number_of_tracks_in_this_hour = n_distinct(dataset_ID,tp,TrackID)) %>%
    ungroup()


# unique(imported_data$annotation)


```

#plotting functions
```{r, echo=TRUE}

plot_basis <- function(data_to_plot){
  ggplot(data_to_plot,aes(x = p_mean_angle, y = p_mean_velocity))+
    theme_classic()+
    ylab("velocity (mm/s)") + xlab("angular velocity (degree/s)")+
    scale_y_log10()+
    scale_x_continuous(limits=c(0,180))+
    theme(legend.direction="horizontal",
        legend.position = "top",
        strip.background = element_rect(colour = "white", fill = "white"),
        panel.spacing = unit(1, "lines"),
        strip.text.x = element_text(size=25,colour = "black", face = "bold"),
        axis.text.x = element_text(size=30),
        axis.title.x = element_text(size=45),
        axis.text.y = element_text(size=35),
        axis.title.y = element_text(size=45))+
    facet_wrap(vars(annotation,dataset_ID,hours_rounded),ncol=length(unique(data$hours_rounded)),scales="free_x")
}


plot_scatterpoints <- function(data_to_plot){
   plot_basis(data_to_plot)+
     geom_point(shape=21, fill="grey",alpha=0.25)
}


plot_scatterdensity <- function(data_to_plot){
  plot_basis(data_to_plot)+
    stat_density_2d(aes(fill = ..ndensity..), geom = "raster", contour = FALSE) +
    geom_rug(col="black",alpha=.01)+
    scale_fill_gradient(low="white",high="black")
}

```


#plot all 10s windows per annotation AND dataset_ID (both as points and density)
```{r, echo=TRUE}

save_path <- file.path(base_path,"plots","scatterpoints")
dir.create(save_path)


for (a in unique(data$annotation)){
  data_to_plot <- data %>%
    filter(annotation == a)
  
  
  plot_scatterpoints(data_to_plot)+
     ggsave(file.path(save_path,paste0("scatterpoints_",a,".png")),height=15,width=35)
  
}


save_path <- file.path(base_path,"plots","scatterdensity")
dir.create(save_path)

for (a in unique(data$annotation)){
  data_to_plot <- data %>%
    filter(annotation == a)

  plot_scatterdensity(data_to_plot)+
    scale_fill_viridis(option = "turbo")+
    ggsave(file.path(save_path,paste0("scatterdensity_",a,".png")),height=15,width=35)

}
```


#plot the relative density for all annotations, timepoints and datasets
#additionally also as seperate file for every annotation
```{r, echo=TRUE}
save_path <- file.path(base_path,"plots","scatterdensity")
dir.create(save_path)
plot_scatterdensity(data)+
  facet_wrap(vars(annotation,hours_rounded),ncol=length(unique(data$hours_rounded)),scales="free_x")+
  ggsave(file.path(save_path,paste0("scatterdensity_all",".png")),bg="black",height=30,width=40)

plot_scatterdensity(data)+
  facet_wrap(vars(annotation,hours_rounded),ncol=length(unique(data$hours_rounded)),scales="free_x")+
  scale_fill_viridis(option = "inferno")+
  ggsave(file.path(save_path,paste0("scatterdensity_all_inferno",".png")),bg="black",height=30,width=40)

plot_scatterdensity(data)+
  facet_wrap(vars(annotation,hours_rounded),ncol=length(unique(data$hours_rounded)),scales="free_x")+
  scale_fill_viridis(option = "turbo")+
  ggsave(file.path(save_path,paste0("scatterdensity_all_turbo",".png")),bg="black",height=30,width=40)

for (a in unique(data$annotation)){
  data_to_plot <- data %>%
    filter(annotation == a)
  
 plot_scatterdensity(data_to_plot)+
    facet_wrap(vars(annotation,hours_rounded),ncol=length(unique(data$hours_rounded)),scales="free_x")+
    ggsave(file.path(save_path,paste0("scatterdensity_bw_",a,".png")),height=7.5,width=45)
 
 plot_scatterdensity(data_to_plot)+
    facet_wrap(vars(annotation,hours_rounded),ncol=length(unique(data$hours_rounded)),scales="free_x")+
    scale_fill_viridis(option = "turbo")+
    ggsave(file.path(save_path,paste0("scatterdensity_turbo_",a,".png")),height=7.5,width=45)
    
}  

```


#plot the relative density for all annotations, timepoints and datasets
#additionally also as seperate file for every annotation
```{r, echo=TRUE}
library(wesanderson)

#lower velocity limit for mode == roaming
velocity_r <- 0.01
#upper angle limit for mode == roaming
angle_r <-15
# upper velocity limit for mode == still
velocity_s <- 0.001


save_path <- file.path(base_path,"plots","scatterpoints_annotated")
dir.create(save_path)


for (a in unique(data$annotation)){
  data_to_plot <- data %>%
    filter(annotation == a) %>%
    mutate(mode = ifelse(p_mean_velocity > velocity_r & p_mean_angle < angle_r,"roaming","dwelling")) %>%
    mutate(mode=ifelse(p_mean_velocity < velocity_s, "still", mode))
  
  plot_basis(data_to_plot)+
    geom_point(aes(fill=mode),shape=21 ,alpha=0.25)+
    geom_rug(col="black",alpha=.01)+
    scale_fill_manual(values = wes_palette("BottleRocket2"))+
    facet_wrap(vars(annotation,hours_rounded),ncol=length(unique(data$hours_rounded)),scales="free_x")+
    ggsave(file.path(save_path,paste0("scatterpoints_annotated_",a,".png")),height=7.5,width=45)
    
}  

```


