
#Select files to load
#We need the clustering file containing the mean positions of each cluster as well as the skeletons filtered file with clusters attached
```{r, include=FALSE}

base_path <-"/media/fpreuss/raid5/timelapses/analysis/200612/"
target_folder <-file.path(base_path, "data","posture","clustered_1")
```

#Load data (clustered postures) for analysis
```{r, include=FALSE}

skeletons_filtered_clustered_filepath <- list.files(path = target_folder,pattern=".+skeletons_filtered_clustered.RDS",ignore.case = TRUE, full.names = TRUE)
clustering_filepath <- list.files(path = target_folder,pattern="clustering.RDS",ignore.case = TRUE, full.names = TRUE)
cluster_centers_reduced_filepath <- list.files(path = target_folder,pattern="cluster_centers_reduced.RDS",ignore.case = TRUE, full.names = TRUE)

cluster <- readRDS(clustering_filepath)
cluster_centers_reduced <- readRDS(cluster_centers_reduced_filepath)
skeleton_data_clustered <- readRDS(skeletons_filtered_clustered_filepath)
```


#calculate relative occurence of clusters
```{r, include=FALSE}

#add clusters to initial skeleton dataset that was used for kmeans clustering
#also calculate relative occurences of postures (i.e. clusters) both total and per annotation
freq_postures <- skeleton_data_clustered %>%
  #select only relevant columns
  select(newID,annotation) %>%
  #do this now for every newID and annotation independently
  group_by(newID, annotation) %>%
  summarise(counts_annotation = n()) %>%
  #do this now for every annotation independently
  group_by(annotation) %>%
  #occurences of all clusters together == total_annotation
  mutate(total_annotation = sum(counts_annotation)) %>%
  mutate(perc_annotation = counts_annotation/total_annotation * 100) %>%
  group_by(newID) %>%
  mutate(counts_all = sum(counts_annotation)) %>%
  mutate(total_all = sum(total_annotation)) %>%
  ungroup() %>%
  mutate(perc_all = counts_all/total_all * 100)
```


#calculate posture occurences
```{r, include=FALSE}
freq_postures_overall <- freq_postures %>%
  group_by(newID,perc_all) %>%
  summarise() %>%
  arrange(desc(perc_all)) %>%
  ungroup() %>%
  mutate(rank_all = 1:n())

ggplot(freq_postures_overall,aes(x=rank_all,y=perc_all))+
  geom_col()+
  labs(x="Posture Rank", y="Probability (%)")+
  theme_linedraw()
  

#order by overall occurence
order_overall <- freq_postures_overall$newID


```

#Plot every frame of a random track
#plotted will be the original skeleton (with original X and Y location), as well as the alligned skeleton and the corresponding posture
```{r, include=FALSE}

save_path <- file.path(base_path,"plots","posture","posture_comparison_plots")
dir.create(save_path)

plot_posture_examples <- function(data_to_plot,X,Y){
  ggplot(data_to_plot, aes_string(x=X,y=Y,color="angle"))+
    geom_point(size=0.75) +
    geom_path(size=2,lineend = "round") +
    theme_void()+
    coord_fixed(ratio = 1)+
    scale_color_gradient2(low = "deepskyblue", mid = "lavender",
                          high = "deeppink",midpoint=0,limits=c(-1,1),na.value="grey") +
    # scale_color_viridis(option = "plasma",limits=c(-1,1))+
    theme(plot.title = element_text(face = "bold"))
  
}

#list of all tracks
list_of_tracks <- skeleton_data_clustered %>%
  mutate(dataset_TrackID =  paste0(dataset_ID,"_",tp,"_",TrackID)) %>%
  distinct(dataset_TrackID) %>%
  pull(dataset_TrackID)


#select a random track from this list
random_track <- sample(list_of_tracks,1)

                                      
#subset random track and turn the skeletons
skeleton_data_clustered_subset <- skeleton_data_clustered %>%
  mutate(dataset_TrackID =  paste0(dataset_ID,"_",tp,"_",TrackID)) %>%
  filter(dataset_TrackID == random_track) %>%
  group_by(ID) %>%
  #keep old X and Y positions (before turning) to compare when plotting
  mutate(X_original = X, Y_original = Y) %>%
  group_modify(~ turn_worm(.x))
  


#plot all frames from list of frames of the random track
for (i in unique(skeleton_data_clustered_subset$frame)){
   
  selected_frame <- i 
  #temporary subset (only skeleton of selected frame)
  skeleton_data_clustered_subset_temp <- skeleton_data_clustered_subset %>%
    filter(frame == selected_frame)
  
  #clusterID of selected skeleton
  clusterID_to_plot <- unique(skeleton_data_clustered_subset_temp$clusterID)
  #corresponding cluster center
  cluster_centers_reduced_temp <- cluster_centers_reduced %>%
    filter(clusterID == clusterID_to_plot)
  
  #plot raw with old X and Y coordinates
  plot_raw <- plot_posture_examples(skeleton_data_clustered_subset_temp, "X_original", "Y_original")+
   geom_point(data=filter(skeleton_data_clustered_subset_temp,index == 2), aes_string("X_original","Y_original"),color="orange",size=8,shape=16) + 
    theme(plot.caption = element_text(vjust = -3),
          legend.position = "none")+
    ggtitle(paste0("Raw ", random_track,", frame ", selected_frame))
    
  #plot turned worm
  plots_alligned <- plot_posture_examples(skeleton_data_clustered_subset_temp,"X","Y") +
    geom_point(data=filter(skeleton_data_clustered_subset_temp,index == 2), aes(X,Y),color="orange",size=5,shape=16) +
    ggtitle(paste0("Alligned"))+
    theme(plot.caption = element_text(vjust = -3),
          legend.position = "none")
  
  #plot corresponding cluster center
  plot_corresponding_cluster_mean <- plot_posture_examples(cluster_centers_reduced_temp,"X","Y") +
    geom_point(data=filter(cluster_centers_reduced_temp,index == 2), aes_string("X","Y"),color="orange",size=5,shape=16) +
    ggtitle(paste0("Posture ", clusterID_to_plot))+
    theme(plot.caption = element_text(vjust = -3),
          legend.position = "none")
  
  #bring all together
  ((plot_raw + plot_spacer()) |
    plots_alligned/
    plot_corresponding_cluster_mean) +
    plot_layout(heights = unit(c(6,1,8,8), c('cm', 'cm','cm','cm')))+
    # plot_layout(widths=c(1,3,3), heights = c(1,3, 3))
     ggsave(file.path(save_path,paste0("posture_frame",selected_frame,".png")),height=15,width=10)

}

```


#Calculate relative occurence of postures per hour
```{r, include=FALSE}

angle_data_postures_first <-  skeleton_data_clustered %>%
  mutate(minutes = 10 + ((tp-1)*8+(tp-1)*0)) %>%
  #round to half hour steps
  mutate(hours_rounded = ceiling(minutes/60*2)/2) %>%
  #round to full hour steps
  # mutate(hours_rounded = ceiling(minutes/60)) %>%
  mutate(dataset_TrackID =  paste0(dataset_ID,"_",tp,"_",TrackID)) %>%
  ###
  # group_by(annotation,dataset_TrackID,hours_rounded) %>%
  # nest() %>%
  # group_by(annotation,hours_rounded) %>%
  # sample_n(80) %>%
  # unnest(cols=c(data)) %>%
  ## group_by(annotation,hours_rounded,dataset_TrackID) %>%
  ## summarise(n_tracks = n_distinct(dataset_TrackID),n_total = n())
  # group_by(annotation,ID,dataset_TrackID,hours_rounded) %>%
  # nest() %>%
  # group_by(annotation,hours_rounded,dataset_TrackID) %>%
  ## summarise(n=n_distinct(ID))
  # sample_n(20) %>%
  # unnest(cols=c(data)) %>%
  # group_by(annotation,hours_rounded) %>%
  # summarise(n_tracks = n_distinct(dataset_TrackID),n_postures = n_distinct(ID))
  ###
  #reduce dataset
  group_by(ID,newID,annotation,hours_rounded,dataset_ID,dataset_TrackID) %>%
  summarise() %>%
  #do this for every newID, timepoint and annotation
  group_by(newID,hours_rounded,annotation) %>%
  #number of clusters per timepoint and experiment
  mutate(number_of_cluster_members_per_tp=n_distinct(ID)) %>%
  group_by(newID,hours_rounded,annotation,dataset_ID) %>%
  #number of clusters per timepoint and experiment
  mutate(number_of_cluster_members_per_tp_per_dataset=n_distinct(ID)) %>%
  arrange(newID) %>%
  #do this for every timepoint and annotation
  group_by(hours_rounded,annotation) %>%
  #total number of postures per timepoint and annotation
  mutate(postures_per_tp=n_distinct(ID)) %>%
  #total number of tracks per timepoint and annotation
  mutate(tracks_per_tp=n_distinct(dataset_TrackID)) %>%
  #percentage per annotation
  mutate(perc = number_of_cluster_members_per_tp/postures_per_tp) %>%
  #do this for every timepoint and annotation
  group_by(hours_rounded,dataset_ID) %>%
  #total number of postures per timepoint and dataset_ID
  mutate(postures_per_tp_per_dataset=n_distinct(ID)) %>%
  #total number of tracks per timepoint and dataset_ID
  mutate(tracks_per_tp_per_dataset=n_distinct(dataset_TrackID)) %>%
  #percentage per dataset_ID  
  mutate(perc_per_dataset = number_of_cluster_members_per_tp_per_dataset/postures_per_tp_per_dataset) %>%
  group_by_at(vars(-ID,-dataset_TrackID)) %>%
  summarise() %>%
  ungroup()

#Posture quantified over time per annotation (i.e. type of experiment)
angle_data_postures <- angle_data_postures_first %>%
  select(-dataset_ID) %>%
  select(-contains("per_dataset")) %>%
  group_by_all() %>%
  summarise() %>%
  #do this for every cluster and annotation  (i.e. over all timepoints)
  group_by(newID,annotation) %>%
  mutate(sd_perc = sd(perc)) %>%
  mutate(rM = rollmean(perc, 2, fill=NA)) %>%
  mutate(sd_rM = sd(rM,na.rm = TRUE)) %>%
  mutate(mean_perc = mean(perc)) %>%
  mutate(mean_rM = mean(rM, na.rm=TRUE)) %>%
  mutate(perc_norm = (perc-mean_perc)/sd_perc) %>%
  mutate(rM_norm = (rM-mean_rM)/sd_rM) %>%
  ungroup() %>%
  filter(hours_rounded <= 9) %>%
  arrange(newID,hours_rounded,annotation) %>%
  group_by(hours_rounded,annotation) %>%
  mutate(tracks_per_hours_rounded = first(tracks_per_tp))

#Posture quantified over time per dataset_ID (i.e. per experiment replicate)
angle_data_postures_per_dataset <- angle_data_postures_first %>%  
  #do this for every cluster and dataset_ID (not grouped as annotation)  (i.e. over all timepoints)
  group_by(newID,dataset_ID) %>%
  mutate(sd_perc_per_dataset = sd(perc_per_dataset)) %>%
  mutate(rM_per_dataset = rollmean(perc_per_dataset, 2, fill=NA)) %>%
  mutate(sd_rM_per_dataset = sd(rM_per_dataset,na.rm = TRUE)) %>%
  mutate(mean_perc_per_dataset = mean(perc_per_dataset)) %>%
  mutate(mean_rM_per_dataset = mean(rM_per_dataset, na.rm=TRUE)) %>%
  mutate(perc_norm_per_dataset = (perc_per_dataset-mean_perc_per_dataset)/sd_perc_per_dataset) %>%
  mutate(rM_norm_per_dataset = (rM_per_dataset-mean_rM_per_dataset)/sd_rM_per_dataset) %>%
  ungroup() %>%
  filter(hours_rounded <= 9) %>%
  arrange(newID,hours_rounded,annotation,dataset_ID)

```



#Plot heatmaps for relative occurence of posture
#for each dataset will be ploted:
#  Heatmap combining all datasets with posture overview (in right order after hierarchical clustering of temporally resolved frequencies)
#  Individual heatmaps for each dataset and also for both datasets together
#  All of the two above with different ways of calculating frequencies:
#  1- frequency
#  2- frequency, normalized (z-score)
#  3- frequency, normalized (z-score) with rolling mean
```{r, include=FALSE}

save_path <- file.path(base_path,"plots","posture","heatmaps")
dir.create(save_path)

plot_posture_heatmap <- function(data_to_plot,order){
  ggplot(data_to_plot,aes(x=factor(newID,levels=order),y=hours_rounded))+
  theme_classic()+
  labs(x="posture IDs",y = "hours",fill="Z-score") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(axis.text.y = element_text(size = 30,face = "bold"),
        axis.text.x = element_text(size = 30),
        axis.title.x = element_text(size=45),
        axis.title.y = element_text(size=45),
        strip.text = element_text(size=45),
        legend.text=element_text(size=50),
        legend.title = element_text(size=50),
        legend.key.size = unit(2, "cm"),
        legend.position = "right",
        legend.direction='vertical')+
  coord_equal()
}

plot_posture_examples <- function(data_to_plot,X,Y){
  ggplot(data_to_plot, aes_string(x=X,y=Y,color="angle"))+
    geom_point(size=6) +
    geom_path(size=5,lineend = "round") +
    theme_void()+
    coord_fixed(ratio = 1)+
    scale_color_gradient2(low = "deepskyblue", mid = "lavender",
                          high = "deeppink",midpoint=0,limits=c(-1,1),na.value="grey") +
    # scale_color_viridis(option = "plasma",limits=c(-1,1))+
    theme(plot.title = element_text(face = "bold"))
}

#get all annotations
annotations <- list(unique(angle_data_postures$annotation)[2],unique(angle_data_postures$annotation)[1],c(rev(unique(angle_data_postures$annotation))))
normalizations <- c("perc","perc_norm","rM_norm")


for (a in annotations){
  for (n in normalizations){
  #prepare clustering
  temporal_clustering <- angle_data_postures %>%
    filter(annotation %in% a[1]) %>%
    na.omit() %>%
    dcast(newID ~ hours_rounded,value.var = n) %>%
    tibble::column_to_rownames(var = "newID")
  
  #cluster the temporal posture patterns with the current normalization
  temporal_clustering <- temporal_clustering[order(as.numeric(rownames(temporal_clustering))),,drop=FALSE]
  #this ordering from the hclsut is the rowID, it is NOT the actual posture ID
  ordering <- hclust(dist(temporal_clustering, method = "euclidean"), method = "average")$order
  #get posture ID by their rownumber 
  ordering <- as.numeric(rownames(temporal_clustering)[ordering])
  
  #generate heatmap data
  #normaliazion column will be the one for the current normalization
  heatmap_data_to_plot <- angle_data_postures %>%
    filter(annotation %in% a) %>%
    rename(normalization =  all_of(n)) %>%
    ungroup() %>%
    mutate(hours_rounded_w_numbers = paste0(hours_rounded, " (",tracks_per_hours_rounded,")"))
  
  #check if the current selected annotation(s) is one or several
  #if only one annotation then we plot hours_rounded_w_numbers as y axis
  if(length(a) == 1){
    #generate heatmap
    heatmap <- ggplot(heatmap_data_to_plot,aes(x=factor(newID,levels=ordering),y=hours_rounded_w_numbers))+
      theme_classic()+
      labs(x="posture IDs",y = "hours",fill="Z-score") +
      scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
      theme(axis.text.y = element_text(size = 30,face = "bold"),
          axis.text.x = element_text(size = 30),
          axis.title.x = element_text(size=45),
          axis.title.y = element_text(size=45),
          strip.text = element_text(size=45),
          legend.text=element_text(size=50),
          legend.title = element_text(size=50),
          legend.key.size = unit(2, "cm"),
          legend.position = "right",
          legend.direction='vertical')+
      coord_equal()+
      geom_tile(aes(fill=normalization))+
      scale_fill_distiller(type = "div",limits=c(-1,1) * max(abs(select(heatmap_data_to_plot,normalization))))
  }else{
    #if multiple annotations we facet_wrap by annotation and plot hours_rounded as y to have a common y axis between annotations
    heatmap <- ggplot(heatmap_data_to_plot,aes(x=factor(newID,levels=ordering),y=hours_rounded))+
      theme_classic()+
      labs(x="posture IDs",y = "hours",fill="Z-score") +
      scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
      theme(axis.text.y = element_text(size = 30,face = "bold"),
          axis.text.x = element_text(size = 30),
          axis.title.x = element_text(size=45),
          axis.title.y = element_text(size=45),
          strip.text = element_text(size=45),
          legend.text=element_text(size=50),
          legend.title = element_text(size=50),
          legend.key.size = unit(2, "cm"),
          legend.position = "right",
          legend.direction='vertical')+
      coord_equal()+
      facet_wrap(vars(annotation),ncol=2)+
      geom_tile(aes(fill=normalization))+
      scale_fill_distiller(type = "div",limits=c(-1,1) * max(abs(select(heatmap_data_to_plot,normalization))))
  }  
  #generate heatmap data per dataset
  heatmap_data_to_plot_per_dataset <- angle_data_postures_per_dataset %>%
    ungroup() %>%
    filter(annotation %in% a)  %>%
    rename(normalization_per_dataset =  paste0(all_of(n),"_per_dataset"))
  
 plot_posture_heatmap(heatmap_data_to_plot_per_dataset,ordering) +
    geom_tile(aes(fill= normalization_per_dataset))+
    scale_fill_distiller(type = "div",limits=c(-1,1) * max(abs(select(heatmap_data_to_plot_per_dataset,normalization_per_dataset))))+
    # scale_fill_distiller(palette="PiYG",limits=c(-1,1) * max(abs(select(heatmap_data_to_plot_per_dataset,normalization_per_dataset))))+
    facet_wrap(vars(dataset_ID),ncol=1)+
    scale_y_continuous(breaks=seq(1,max(heatmap_data_to_plot_per_dataset$hours_rounded),2))+
    ggsave(file.path(save_path,paste0("200511_heatmap_",paste0(a,collapse="+"),"_",n,"_per_dataset",".png")),width=49,height=30)
  
  #levels must be changed for ggplot to take new order into account
  cluster_centers_reduced$newID = factor(cluster_centers_reduced$newID, levels=ordering)
  
  #generate all postures, for the mirrored ones show only newID_sub
  skeletons <- plot_posture_examples(filter(cluster_centers_reduced,newID_sub == 1), "X","Y") +
    geom_point(data=filter(cluster_centers_reduced,index == 2 & newID_sub == 1), aes(X,Y),color="orange",size=5,shape=17) +
    facet_wrap(vars(newID),ncol=6) +
    theme(strip.text.x = element_text(size = 45,face="bold"))
  
  heatmap /
    skeletons + 
    plot_layout(widths = c(1,4),heights = c(1,4))+
    ggsave(file.path(save_path,paste0("heatmap_",paste0(a,collapse="+"),"_",n,".png")),width=49,height=30)
  
 
  }
}

```


```{r, include=FALSE}
#define color palette for plots
library(wesanderson)
mr3 <- wes_palettes$Moonrise3[3:2]

save_path <- file.path(base_path,"plots","posture","boxplots_posture_freqs")
dir.create(save_path)


#new function to plot posture examples
plot_posture_examples <- function(data_to_plot,X,Y){
  ggplot(data_to_plot, aes_string(x=X,y=Y,color="angle"))+
    geom_point(size=4) +
    geom_path(size=2,lineend = "round") +
    theme_void()+
    coord_fixed(ratio = 1)+
    #add some buffer on y axis to show full skeleton
    scale_y_continuous(limits=c(0,1.1))+
    scale_color_gradient2(low = "deepskyblue", mid = "lavender",
                          high = "deeppink",midpoint=0,limits=c(-1,1),na.value="grey") +
    # scale_color_viridis(option = "plasma",limits=c(-1,1))+
    theme(plot.title = element_text(face = "bold"))
}
#get names of all newIDs
all_IDs <- unique(cluster_centers_reduced$newID)

#for every cluster ID, calculate wilcoxon rank test pvalue between time bins and append to one matrix
all_ps <- NULL
for (i in all_IDs) {
  p <- angle_data_postures_per_dataset %>%
    #only one clusterID
    filter(newID == i) %>%
    #only for timepoints lower than 6 hours
    filter(hours_rounded <= 6) %>%
    #create time bins
    mutate(time_bin = ifelse(hours_rounded <= 3, "< 3","> 3")) %>%
    #calculate pvalue for only annotation
    filter(annotation == "N2 RT no food") %>%
    select(perc_per_dataset,time_bin) %>%
    #use the perc_per_dataset for calculation
    summarise(Wilcox = wilcox.test(perc_per_dataset~time_bin, data=., paired=FALSE)$p.value) %>%
    mutate(newID = i) %>%
    mutate(Wilcox = as.numeric(Wilcox))
  
  all_ps <- rbind(all_ps, p)
}

all_ps %>%
  arrange(Wilcox) %>%
  slice(1:30)

#take the clusterIDs with the lowest pvalue
significant_IDs <- all_ps %>%
  arrange(Wilcox) %>%
  slice(1:30) %>%
  pull(newID)

#for all IDs plot boxplot and corresponding plosture
for (i in all_IDs){
  
  pvalue <- all_ps %>%
    filter(newID == i) %>%
    select(Wilcox) %>%
    pull()
  
  data_to_plot <- angle_data_postures_per_dataset %>%
    filter(newID %in% i) %>%
    #only for timepoints lower than 6 hours
    filter(hours_rounded <= 6) %>%
    mutate(time_bin = ifelse(hours_rounded <= 3, "< 3h","> 3h")) %>%
    #frequency * 1000
    mutate(perc_per_dataset = perc_per_dataset * 1000)
  
  data_to_plot$annotation <- factor(data_to_plot$annotation, levels=rev(unique(data_to_plot$annotation)))
  
  boxplots <- ggplot(data_to_plot, aes(x=time_bin, y=perc_per_dataset))+
   geom_boxplot(aes(fill=annotation),lwd=1.2,outlier.shape=NA)+
   geom_point(aes(fill=annotation),position = position_jitterdodge(),shape=21,size=2.5)+
   xlab("hours") + ylab("frequency / 1000")+
    scale_fill_manual(values=mr3)+
    theme_classic()+
    theme(
      legend.direction="vertical",
      legend.position = "right",
      strip.background = element_rect(colour = "white", fill = "white"),
      panel.spacing = unit(1, "lines"),
      strip.text.x = element_text(size=15,colour = "black", face = "bold"),
      axis.text.x = element_text(size=30),
      axis.title.x = element_text(size=20),
      axis.text.y = element_text(size=30),
      axis.title.y = element_text(size=20),
      axis.ticks=element_line(size=1.5),
      axis.ticks.length=unit(0.25,"cm"),
      axis.line = element_line(colour = 'black', size = 1.5),
      legend.key.size = unit(2.5, "cm"))
  
  skeletons <- plot_posture_examples(filter(cluster_centers_reduced,newID %in% i & newID_sub == 1), "X","Y") +
    geom_point(data=filter(cluster_centers_reduced,index == 2 & newID == i & newID_sub == 1), aes(X,Y),color="orange",size=5,shape=17)+
    ggtitle(paste0("posture_",i,"\npvalue= ",round(pvalue,10)))
  
  boxplots + skeletons +
    plot_layout(heights = unit(c(5, 1), c('cm', 'null')))+
    ggsave(file.path(save_path,paste0("boxplot_freq_posture_",i,".png")),width=7,height=5)
  
}


```

#calculate ngrams
#i.e. which posters occur often together in a sequence
```{r, include=FALSE}
library(tidytext)

save_path <- file.path(base_path,"plots","posture","syntax")
dir.create(save_path)


#reduce skeleton_data_clustered for one row per track
postures_per_track <- skeleton_data_clustered %>%
  group_by(annotation,dataset_ID,tp,TrackID,frame,ID,newID) %>%
  summarise()

#if same posture occurs in two subsequent frames, these are collapsed to one row
postures_per_track <- postures_per_track[cumsum(rle(postures_per_track$newID)$lengths),] %>%
  group_by(annotation,dataset_ID,tp,TrackID) %>%
  #all postures of one track (within dataset and tp) to one row
  summarise(postures = paste(newID, collapse = ' '))

#calculate ngrams individually for each track (within dataset and tp)
posture_trigrams <- postures_per_track %>%
  group_by(annotation,dataset_ID,tp,TrackID) %>%
  unnest_tokens(trigrams, postures, token = "ngrams", n = 3) %>%
  ungroup()

#counting frequency of postures
posture_trigrams_stats <- posture_trigrams %>%
  mutate(minutes = 10 + ((tp-1)*8+(tp-1)*0)) %>%
  #round to half hour steps
  mutate(hours_rounded = ceiling(minutes/60*2)/2) %>%
  #count number of unique trigrams per dataset and hours_rounded
  group_by(annotation,dataset_ID,hours_rounded) %>%
  mutate(total_trigrams_per_dataset_per_hours_rounded = n_distinct(trigrams)) %>%
  #absolute occurences of one trigram per unique dataset and hours_rounded
  group_by(annotation,dataset_ID, hours_rounded,total_trigrams_per_dataset_per_hours_rounded, trigrams) %>%
  summarise(occurences_trigram=n()) %>%
  #relative occurence of one trigram per unique dataset and hours_rounded
  mutate(freq_trigram_per_dataset = occurences_trigram/total_trigrams_per_dataset_per_hours_rounded) %>%
  #same is calculated now over datasets just by annotation (i.e. type of experiment)
  group_by(annotation, hours_rounded,trigrams) %>%
  mutate(trigram_per_hours_rounded = sum(occurences_trigram)) %>%
  mutate(total_trigrams_per_hours_rounded = sum(total_trigrams_per_dataset_per_hours_rounded)) %>%
  #relative occurence of one trigram per hours_rounded
  mutate(freq_trigram = trigram_per_hours_rounded/total_trigrams_per_hours_rounded) %>%
  select(annotation, hours_rounded,trigrams,dataset_ID, everything()) %>%
  group_by(annotation,hours_rounded) %>%
  #highest freq_trigram across datasets per hours_rounded (within one experiment type)
  filter(freq_trigram == max(freq_trigram)) %>%
  #if two trigrams have the same relative frequency (over all datasets), take only first one
  slice(1) %>%
  #split trigram
  group_by(annotation,hours_rounded) %>%
  separate(trigrams, c("p1", "p2", "p3"), sep = " ") %>%
  gather(trigram_position, posture, p1:p3) %>%
  mutate(posture=as.numeric(posture)) %>%
  group_by(annotation,hours_rounded,trigram_position,posture,total_trigrams_per_hours_rounded,trigram_per_hours_rounded,freq_trigram) %>%
  summarise()

posture_trigrams_w_postures <- posture_trigrams_stats %>%
  #add cluster centers for each trigram
  left_join(cluster_centers_reduced,by=c("posture" = "newID")) %>%
  filter(newID_sub == 1) %>%
  select(-c(clusterID, mirroredID, newID_sub)) %>%
  arrange(annotation, hours_rounded,trigram_position,freq_trigram) %>%
  mutate(ID = paste(annotation, hours_rounded,trigram_position,posture,sep="\n"))
 
#make order consistent
posture_trigrams_w_postures$ID <- factor(posture_trigrams_w_postures$ID, levels=sort(unique(posture_trigrams_w_postures$ID)))



ggplot(posture_trigrams_w_postures, aes(x=X,y=Y,color=angle))+
  geom_point(size=2) +
  geom_path(size=1,lineend = "round") +
  theme_void()+
  coord_fixed(ratio = 1)+
  scale_color_gradient2(low = "deepskyblue", mid = "lavender",
                          high = "deeppink",midpoint=0,limits=c(-1,1),na.value="grey") +
  geom_point(data=filter(posture_trigrams_w_postures,index == 2), aes(X,Y),color="orange",size=5,shape=17) +
  facet_wrap(vars(ID),ncol=3) +
  ggsave(file.path(save_path,paste0("trigrams_per_annotation",".png")),width=10,height=40)
  
```
