
  
#Define locations and datasets to include
```{r, echo=FALSE}
#bins or tracks?
average <- "bins"
  
base_path <- "/media/fpreuss/raid5/timelapses/analysis/200703"
```

#Input: Data from "plots_motion_analysis_scatter.Rmd"
#Please excecute this first!
```{r, echo=TRUE}
  
#define colors
library(wesanderson)


#lower velocity limit for mode == roaming
velocity_r <- 0.01
#upper angle limit for mode == roaming
angle_r <- 30
#upper velocity limit for mode == still
# velocity_s <- 0.005

  
data_binarized <- data %>%
  mutate(mode = ifelse(p_mean_velocity > velocity_r & p_mean_angle < angle_r,"roaming","dwelling")) %>%
  group_by(dataset_ID, tp, TrackID, binning) %>%
  mutate(omega = ifelse(p_omega_rf > 0, 1, 0))

#here we will summarise by tp (==video timestep)
#so later in the plots one dot = one (in our case 8 mins long) video 
data_bs <- data_binarized %>%
  group_by(annotation,hours_rounded,tp,mode,dataset_ID) %>%
  #summarise over tp
  #this will be the mean of the bins contained within that tp and mode
  #counts is the number of bins of a certain mode
  #mean_omega is the number of bins with at least one detected omega turn divided by the total number of bins
  summarise(counts=n(),mean_velocity = mean(p_mean_velocity), mean_angle = mean(p_mean_angle),perc_omega = sum(omega)/n()) %>%
  group_by(annotation,hours_rounded,tp,dataset_ID) %>%
  #total counts
  mutate(sum=sum(counts)) %>%
  #relative occurence of mode
  mutate(perc = counts/sum) %>%
  ungroup()
  

# data_bsh <- data_binarized %>%
#   group_by(annotation,hours_rounded,mode,dataset_ID) %>%
#   mutate(counts=n()) %>%
#   #total counts
#   group_by(annotation,hours_rounded,dataset_ID) %>%
#   mutate(sum=sum(counts)) %>%
#   #relative occurence of mode
#   mutate(perc = counts/sum) %>%
#   group_by(annotation, hours_rounded, dataset_ID,mode) %>%
#   summarise(mean_mode_perc = mean(perc),mean_velocity = mean(p_mean_velocity), mean_angle = mean(p_mean_angle))



```
#function for plotting mean mode fraction with Local Polynomial Regression Fitting
```{r, echo=TRUE}

plot_mean_modes <- function(data,grouping){
  ggplot(data, aes_string(x="hours_rounded", y="perc", group=grouping,color=grouping,fill=grouping))+
  # geom_point(size=1,alpha=0.5, shape=21, aes(fill=mode),color="black")+
  geom_smooth(alpha=0.5)+
  scale_x_continuous(breaks=(seq(1,show_until)))+
  theme_classic()+
  labs(x="time (hours)", "relative fraction")+
  scale_fill_manual(values =pal)+
  scale_color_manual(values =pal)+
  theme(legend.direction="horizontal",
        legend.position = "top",
        strip.background = element_rect(colour = "white", fill = "white"),
        panel.spacing = unit(1, "lines"),
        strip.text.x = element_text(size=15,colour = "black", face = "bold"),
        axis.text.x = element_text(size=10),
        axis.title.x = element_text(size=25),
        axis.text.y = element_text(size=15),
        axis.title.y = element_text(size=25))
}
```

#plot modes
```{r, echo=TRUE}
save_path <- file.path(base_path,"plots","bins","comparisons")
dir.create(save_path)

pal <- wes_palette("Rushmore1")[c(4,5)]
#roaming and dwelling
data_bs %>%
  plot_mean_modes(.,"mode")+
    facet_wrap(vars(annotation),ncol=3,scales="free_x")+
    ggsave(file.path(save_path,paste0("modes_relative.png")),height=7.5,width=10,dpi=600)

pal <- wes_palette("Rushmore1")[c(4)]
#only roaming
data_bs %>%
  filter(mode %in% c("dwelling")) %>%
  plot_mean_modes(.,"mode")+
    facet_wrap(vars(annotation),ncol=3,scales="free_x")+
    ggsave(file.path(save_path,paste0("dwelling_relative.png")),height=7.5,width=10,dpi=600)

pal <- wes_palette("Rushmore1")[c(5)]
#only roaming
data_bs %>%
  filter(mode %in% c("roaming")) %>%
  plot_mean_modes(.,"mode")+
    facet_wrap(vars(annotation),ncol=3,scales="free_x")+
    ggsave(file.path(save_path,paste0("roaming_relative.png")),height=7.5,width=10,dpi=600)


pal <-wes_palette("Darjeeling1")
#only roaming
data_bs %>%
  filter(mode %in% c("roaming")) %>%
  filter(annotation %in% c(
    "Agar",
    "OP50",
    "OP50 with Az NGM"
  )) %>%
  plot_mean_modes(.,"annotation")+
    ggsave(file.path(save_path,paste0("roaming_relative.png")),height=7.5,width=10,dpi=600)


```

#plot relative occurence of dwelling AND roaming for all timepoints for all conditions -- BOXPLOT
```{r, echo=TRUE}

for (a in unique(data$annotation)){
  data_to_plot <- data_bs %>%
    filter(annotation == a)
  
  ggplot(data_to_plot,aes(x=factor(hours_rounded,levels=unique(hours_rounded)),y=perc,fill=mode))+
        geom_boxplot(aes(fill=mode),width=0.75,lwd=1.2,alpha=0.75,outlier.size = 0)+
        geom_point(aes(group=mode,fill=mode),position=position_jitter(width=0.25),shape=21, color="black",size=1.5)+
        scale_y_continuous(limits=c(0,1))+
        scale_fill_manual(values =pal)+
        xlab("hours") + ylab("Relative occurence of \nbehavioral state")+
        facet_wrap(vars(mode),ncol=3)+
        theme_classic()+
        theme(legend.direction="horizontal",
          legend.position = "top",
          strip.background = element_rect(colour = "white", fill = "white"),
          panel.spacing = unit(1, "lines"),
          strip.text.x = element_text(size=15,colour = "black", face = "bold"),
          axis.text.x = element_text(size=10),
          axis.title.x = element_text(size=25),
          axis.text.y = element_text(size=15),
          axis.title.y = element_text(size=25))+
    ggsave(file.path(save_path,paste0("modes_relative_box_",a,".png")),height=7.5,width=15,dpi=600)
  
}
  
```


#plot relative occurence of dwelling/roaming for specific timepoints and conditions
```{r, echo=TRUE}


se <- function(x) sqrt(var(x)/length(x))

plot_mode_relative <- function(data_bs, selected_mode, selected_hours, selected_annotations){

  data_bsf <- data_bs %>%
    filter(annotation %in% selected_annotations) %>%
    filter(hours_rounded %in% selected_hours) %>%
    filter(mode %in% selected_mode)
  
  data_bsfs <- data_bsf %>%
    group_by(annotation,hours_rounded) %>%
    summarise(
      sd = sd(perc, na.rm=TRUE),
      # sem = se(perc),
      perc = mean(perc)
    )
  
  data_bsf$annotation <- factor(data_bsf$annotation, levels=unique(data_bsf$annotation))
  
  
  ggplot(data_bsf,aes(x=factor(hours_rounded,levels = unique(hours_rounded)),y=perc,fill=annotation))+
        # geom_boxplot(aes(fill=annotation),lwd=1.2, outlier.shape = NA)+
        geom_point(position = position_jitterdodge(),color="black",shape=21,size=2.5,alpha=0.5)+
        geom_pointrange(data = data_bsfs,aes(ymin = perc-sd, ymax = perc+sd),color="black",position = position_dodge(0.75))+
        scale_fill_manual(values=pal)+
        xlab("hours") + ylab(paste0("fraction ",selected_mode))+
        theme_classic()+
        theme(
          legend.direction="horizontal",
          legend.position = "top",
          strip.background = element_rect(colour = "white", fill = "white"),
          panel.spacing = unit(1, "lines"),
          strip.text.x = element_text(size=15,colour = "black", face = "bold"),
          axis.text.x = element_text(size=30),
          axis.title.x = element_text(size=20),
          axis.text.y = element_text(size=30),
          axis.title.y = element_text(size=20),
          axis.ticks=element_line(size=1.5),
          axis.ticks.length=unit(0.25,"cm"),
          axis.line = element_line(colour = 'black', size = 1.5))

}



selected_mode <- "dwelling"
selected_hours <- c(6,7,8,9,10,11,12)
pal <- wes_palette("Darjeeling1")[c(5,1)]
selected_annotations <- c("OP50 with Az NGM","OP50")

plot_mode_relative(data_bs, selected_mode, selected_hours, selected_annotations)+
  ggsave(file.path(save_path,paste0("relative_compare_",paste(selected_annotations, collapse="_"),".png")),height=5,width=7.5,dpi=600)

selected_hours <- unique(data_bs$hours_rounded)
plot_mode_relative(data_bs, selected_mode, selected_hours, selected_annotations)+
  ggsave(file.path(save_path,paste0("relative_compare_",paste(selected_annotations, collapse="_"),"_all_hours.png")),height=5,width=12,dpi=600)




selected_annotations <- c("Agar", "OP50")
selected_hours <- c(6,7,8,9,10,11,12)
pal <- wes_palette("Darjeeling1")[c(1,5)]
plot_mode_relative(data_bs, selected_mode, selected_hours, selected_annotations)+
  ggsave(file.path(save_path,paste0("relative_compare_",paste(selected_annotations, collapse="_"),".png")),height=5,width=7.5,dpi=600)

selected_hours <- unique(data_bs$hours_rounded)
plot_mode_relative(data_bs, selected_mode, selected_hours, selected_annotations)+
  ggsave(file.path(save_path,paste0("relative_compare_",paste(selected_annotations, collapse="_"),"_all_hours.png")),height=5,width=12,dpi=600)




```

#function for plotting histograms
```{r, echo=TRUE}
plot_histograms <- function(data,X,xlab){
  ggplot(data,aes_string(x=X,fill="annotation"))+
    geom_histogram(lwd=1.2,binwidth = 0.1)+
    xlab(xlab)+
    theme_classic()+
    scale_fill_manual(values=pal)+
    facet_wrap(vars(annotation,hours_rounded),scales="free")+
      theme(
        legend.direction="horizontal",
        legend.position = "top",
        strip.background = element_rect(colour = "white", fill = "white"),
        panel.spacing = unit(1, "lines"),
        strip.text.x = element_text(size=15,colour = "black", face = "bold"),
        axis.text.x = element_text(size=20),
        axis.title.x = element_text(size=20),
        axis.text.y = element_text(size=20),
        axis.title.y = element_text(size=20),
        axis.ticks=element_line(size=1.5),
        axis.ticks.length=unit(0.25,"cm"),
        axis.line = element_line(colour = 'black', size = 1.5))
      
  
  
}

#function for plotting violin plots
plot_violins <- function(data_bs,Y,ylab){
  
  data_bsf <<- data_bs %>%
    filter(annotation %in% selected_annotations) %>%
    filter(hours_rounded %in% selected_hours) %>%
    filter(mode %in% selected_mode) %>%
    mutate(annotation =  factor(annotation, levels = selected_annotations)) %>%
    arrange(annotation)    
  
  data_bsfs <- data_bsf %>%
    group_by(annotation,hours_rounded) %>%
    summarise(
      sd = sd(!!sym(Y), na.rm=TRUE),
      # sem = se(perc),
      !!Y := mean(!!sym(Y)),
      error_min = !!sym(Y)-sd,
      error_max = !!sym(Y)+sd
    )
    
  
  ggplot(data_bsf,aes_string(x="annotation",y=Y,fill="annotation"))+
    # geom_boxplot(width=0.1, lwd=1.5,color="black")+
    {
      if(length(selected_annotations) > 2) 
    geom_violin(fill="grey", alpha=0.25,lwd=0)
    } +
    geom_point(size=2,shape=21,position = position_jitterdodge(jitter.width = 0.4))+
    geom_pointrange(data = data_bsfs,aes(ymin = error_min, ymax = error_max),position = position_dodge(0.75))+
    scale_y_continuous(limits=c(0,NA))+
    labs(y=paste0(Y, " (", selected_mode,")"))+
    theme_classic()+
    scale_fill_manual(values=pal)+
    facet_wrap(vars(hours_rounded),scales="fixed")+
    theme(
      legend.direction="horizontal",
      legend.position = "top",
      strip.background = element_rect(colour = "white", fill = "white"),
      panel.spacing = unit(1, "lines"),
      strip.text.x = element_text(size=15,colour = "black", face = "bold"),
      axis.text.x = element_text(size=10),
      axis.title.x = element_text(size=20),
      axis.text.y = element_text(size=20),
      axis.title.y = element_text(size=20),
      axis.ticks=element_line(size=1.5),
      axis.ticks.length=unit(0.25,"cm"),
      axis.line = element_line(colour = 'black', size = 1.5))
  
}
```

 
#plot velocity histograms for specific timepoints and conditions
```{r, echo=TRUE}
library(ggsignif)
#for Dunnett's test
library(multcomp)
#for exporting Dunnett's test result
library(broom)

##### Only quantify 10s bins that are stratified as "Roaming" ####
# Agar and OP50
selected_hours <- c(12)
pal <- wes_palette("Darjeeling1")[c(1,5)]
selected_mode <- "roaming"
selected_annotations <- c("Agar","OP50")

data_bs %>%
  plot_violins(., "mean_velocity", "velocity (mm/s)")+
    geom_signif(comparisons = list(c(selected_annotations[1], selected_annotations[2])),map_signif_level = TRUE, textsize=2,test = "wilcox.test") +
    ggsave(file.path(save_path,paste0(selected_mode,"_mean_velocity","_",paste(selected_annotations, collapse="_"),".png")),height=5,width=5)



# OP50 with Az NGM and OP50
selected_hours <- c(12)
pal <- wes_palette("Darjeeling1")[c(2,5)]
selected_mode <- "roaming"
selected_annotations <- c("OP50 with Az NGM","OP50")

data_bs %>%
  plot_violins(., "mean_velocity", "velocity (mm/s)")+
    geom_signif(comparisons = list(c(selected_annotations[1], selected_annotations[2])),map_signif_level = TRUE, textsize=2,test = "wilcox.test") +
    ggsave(file.path(save_path,paste0(selected_mode,"_mean_velocity","_",paste(selected_annotations, collapse="_"),".png")),height=5,width=5)



# MT14984 OP50 and OP50
selected_hours <- c(12)
pal <- wes_palette("Darjeeling1")[c(3,5)]
selected_mode <- "roaming"
selected_annotations <- c("MT14984 OP50","OP50")

data_bs %>%
  plot_violins(., "mean_velocity", "velocity (mm/s)")+
    geom_signif(comparisons = list(c(selected_annotations[1], selected_annotations[2])),map_signif_level = TRUE, textsize=2,test = "wilcox.test") +
    ggsave(file.path(save_path,paste0(selected_mode,"_mean_velocity","_",paste(selected_annotations, collapse="_"),".png")),height=5,width=5)



# daf2 and OP50
selected_hours <- c(12)
pal <- wes_palette("Darjeeling1")[c(4,5)]
selected_mode <- "roaming"
selected_annotations <- c("daf2","OP50")

data_bs %>%
  plot_violins(., "mean_velocity", "velocity (mm/s)")+
    geom_signif(comparisons = list(c(selected_annotations[1], selected_annotations[2])),map_signif_level = TRUE, textsize=2,test = "wilcox.test") +
    ggsave(file.path(save_path,paste0(selected_mode,"_mean_velocity","_",paste(selected_annotations, collapse="_"),".png")),height=5,width=5)


# daf2,Agar,OP50 with Az NGM and OP50
selected_hours <- c(12)
pal <- wes_palette("Darjeeling1")[c(5,4,1,2)]
selected_mode <- "roaming"
selected_annotations <- c("OP50","daf2","Agar","OP50 with Az NGM")

data_bs %>%
  plot_violins(., "mean_velocity", "velocity (mm/s)")+
  ggsave(file.path(save_path,paste0(selected_mode,"_mean_velocity","_",paste(selected_annotations, collapse="_"),".png")),height=5,width=5)

#right order (so that OP50 is first factor and treated as "control" for Dunnett's post-hoc test)
data_bsf$annotation <- relevel(data_bsf$annotation, ref = "OP50")
# Compute the analysis of variance
aov <- aov(mean_velocity ~ annotation, data = data_bsf)
# Summary of the analysis
summary(aov)
# Dunnett's post-hoc test
post_test <- glht(aov,
  linfct = mcp(annotation = "Dunnett")
)
write.table(tidy(post_test),file=file.path(save_path,paste0(selected_mode,"_mean_velocity","_",paste(selected_annotations, collapse="_"),".txt")))


##### Only quantify 10s bins that are stratified as "Dwelling" ####
#MT14984 and OP50
selected_hours <- c(12)
pal <- wes_palette("Darjeeling1")[c(3,5)]
selected_mode <- "dwelling"
selected_annotations <- c("MT14984 OP50","OP50")

data_bs %>%
  plot_violins(., "mean_velocity", "velocity (mm/s)")+
    geom_signif(comparisons = list(c(selected_annotations[1], selected_annotations[2])),map_signif_level = TRUE, textsize=2,test = "wilcox.test") +
    ggsave(file.path(save_path,paste0(selected_mode,"_mean_velocity","_",paste(selected_annotations, collapse="_"),".png")),height=5,width=5)


#daf2 and OP50
selected_hours <- c(12)
pal <- wes_palette("Darjeeling1")[c(4,5)]
selected_mode <- "dwelling"
selected_annotations <- c("daf2","OP50")

data_bs %>%
  plot_violins(., "mean_velocity", "velocity (mm/s)")+
    geom_signif(comparisons = list(c(selected_annotations[1], selected_annotations[2])),map_signif_level = TRUE, textsize=2,test = "wilcox.test") +
    ggsave(file.path(save_path,paste0(selected_mode,"_mean_velocity","_",paste(selected_annotations, collapse="_"),".png")),height=5,width=5)


```


#plot angular velocity histograms for specific timepoints and conditions
```{r, echo=TRUE}


##### Only quantify 10s bins that are stratified as "Roaming" ####
#daf2,Agar,OP50 with Az NGM and OP50
selected_hours <- c(12)
pal <- wes_palette("Darjeeling1")[c(5,4,1,2)]
selected_mode <- "roaming"
selected_annotations <- c("OP50","daf2","Agar","OP50 with Az NGM")

data_bs %>%
  plot_violins(., "mean_angle", "velocity (mm/s)")+
  ggsave(file.path(save_path,paste0(selected_mode,"_mean_angle","_",paste(selected_annotations, collapse="_"),".png")),height=5,width=5)

#right order (so that OP50 is first factor and treated as "control" for Dunnett's post-hoc test)
data_bsf$annotation <- relevel(data_bsf$annotation, ref = "OP50")
# Compute the analysis of variance
aov <- aov(mean_velocity ~ annotation, data = data_bsf)
# Summary of the analysis
summary(aov)
# Dunnett's post-hoc test
post_test <- glht(aov,
  linfct = mcp(annotation = "Dunnett")
)

write.table(tidy(post_test),file=file.path(save_path,paste0(selected_mode,"_mean_angle","_",paste(selected_annotations, collapse="_"),".txt")))



#MT14984 OP50 and OP50
selected_hours <- c(12)
selected_mode <- "roaming"
selected_annotations <- c("OP50", "MT14984 OP50")

data_bs %>%
  plot_violins(., "mean_angle", "angular velocity (°/s)")+
    geom_signif(comparisons = list(c(selected_annotations[1], selected_annotations[2])),map_signif_level = TRUE, textsize=1,test = "wilcox.test") +
    ggsave(file.path(save_path,paste0(selected_mode,"_mean_angle","_",paste(selected_annotations, collapse="_"),".png")),height=5,width=5)



##### Only quantify 10s bins that are stratified as "Dwelling" ####
#MT14984 OP50 and OP50
pal <- wes_palette("Darjeeling1")[c(3,5)]
selected_hours <- c(12)
selected_mode <- "dwelling"
selected_annotations <- c("OP50", "MT14984 OP50")

data_bs %>%
  plot_violins(., "mean_angle", "angular velocity (°/s)")+
    geom_signif(comparisons = list(c(selected_annotations[1], selected_annotations[2])),map_signif_level = TRUE, textsize=1,test = "wilcox.test") +
    ggsave(file.path(save_path,paste0(selected_mode,"_mean_angle","_",paste(selected_annotations, collapse="_"),".png")),height=5,width=5)



#daf2,Agar,OP50 with Az NGM and OP50
selected_hours <- c(12)
pal <- wes_palette("Darjeeling1")[c(5,4,1,2)]
selected_mode <- "dwelling"
selected_annotations <- c("OP50","daf2","Agar","OP50 with Az NGM")

data_bs %>%
  plot_violins(., "mean_angle", "velocity (mm/s)")+
  ggsave(file.path(save_path,paste0(selected_mode,"_mean_angle","_",paste(selected_annotations, collapse="_"),".png")),height=5,width=5)

#right order (so that OP50 is first factor and treated as "control" for Dunnett's post-hoc test)
data_bsf$annotation <- relevel(data_bsf$annotation, ref = "OP50")
# Compute the analysis of variance
aov <- aov(mean_velocity ~ annotation, data = data_bsf)
# Summary of the analysis
summary(aov)
# Dunnett's post-hoc test
post_test <- glht(aov,
  linfct = mcp(annotation = "Dunnett")
)

write.table(tidy(post_test),file=file.path(save_path,paste0(selected_mode,"_mean_angle","_",paste(selected_annotations, collapse="_"),".txt")))


```

```{r, echo=TRUE}


plot_omega <- function(data_bs, selected_mode, selected_hours, selected_annotations){

  data_bsf <<- data_bs %>%
    filter(annotation %in% selected_annotations) %>%
    filter(hours_rounded %in% selected_hours) %>%
    filter(mode %in% selected_mode) %>%
    mutate(annotation = factor(annotation, levels = selected_annotations)) %>%
    arrange(annotation) 
  
  data_bsfs <- data_bsf %>%
    group_by(annotation,hours_rounded) %>%
    summarise(
      sd = sd(perc_omega, na.rm=TRUE),
      # sem = se(perc),
      perc_omega = median(perc_omega)
    )
  
  ggplot(data_bsf,aes(x=factor(hours_rounded,levels = unique(hours_rounded)),y=perc_omega,fill=annotation))+
        geom_boxplot(lwd=1.2,outlier.shape = NA)+
        geom_point(position = position_jitterdodge(jitter.width=0.25),color="black",shape=21,size=2.5,alpha=0.5)+
        # geom_pointrange(data = data_bsfs,aes(ymin = perc_omega-sd, ymax = perc_omega+sd),color="black",position = position_dodge(0.75))+
        scale_fill_manual(values=pal)+
        xlab("hours") + ylab(paste0("fraction omega turns"))+
        theme_classic()+
        theme(
          legend.direction="horizontal",
          legend.position = "top",
          strip.background = element_rect(colour = "white", fill = "white"),
          panel.spacing = unit(1, "lines"),
          strip.text.x = element_text(size=15,colour = "black", face = "bold"),
          axis.text.x = element_text(size=30),
          axis.title.x = element_text(size=20),
          axis.text.y = element_text(size=30),
          axis.title.y = element_text(size=20),
          axis.ticks=element_line(size=1.5),
          axis.ticks.length=unit(0.25,"cm"),
          axis.line = element_line(colour = 'black', size = 1.5))

}
selected_annotations <- c("OP50","Agar","OP50 with Az NGM")
selected_hours <- c(1,12)
pal <- wes_palette("Darjeeling1")[c(5,1,2)]
selected_mode <- "roaming"
plot_omega(data_bs, selected_mode, selected_hours, selected_annotations)+
  ggsave(file.path(save_path,paste0("omega_",paste(selected_annotations, collapse="_"),".png")),height=5,width=5,dpi=600)


# data_bsf is created by the plot_omega function
# create separate dataframe for each timepoint (if two timepoints have been selected)
data_bsf1 <- filter(data_bsf, hours_rounded == selected_hours[1])
data_bsf2 <- filter(data_bsf, hours_rounded == selected_hours[2])

# for every dataframe (i.e. timepoint) compute separate kruskal wallis test
kw1 <- kruskal.test(perc_omega ~ annotation, data = data_bsf1)
kw2 <- kruskal.test(perc_omega ~ annotation, data = data_bsf2)

#select p-value correction for pairwise wilcox test
padjust <- "BH"

#for each timepoint new dataframe with results from pairwise wilcox test and kruskal wallis p value 
post_test1 <- pairwise.wilcox.test(data_bsf1$perc_omega, data_bsf1$annotation,
                 p.adjust.method = padjust) %>%
  tidy() %>%
  mutate(kw_pvalue = kw1$p.value) %>%
  mutate(selected_hour = selected_hours[1])

post_test2 <- pairwise.wilcox.test(data_bsf2$perc_omega, data_bsf2$annotation,
                 p.adjust.method = padjust) %>%
  tidy() %>%
  mutate(kw_pvalue = kw2$p.value) %>%
  mutate(selected_hour = selected_hours[2])

#combine the results of the two wilcox tests and attach methods description
post_test <- rbind(post_test1, post_test2) %>%
  mutate(test = "kruskal-wallis", padjust = padjust)

write.table(post_test,file=file.path(save_path,paste0("omega_",paste(selected_annotations, collapse="_"),".txt")))



```
