#Select paths
```{r, include=FALSE}
base_path <- "/media/fpreuss/raid5/timelapses/analysis/200703/"
target_folder <- "/media/fpreuss/raid5/timelapses/analysis/200703/data/posture/posture_groups/"

```

#Load data for clustering of posture libraries across annotations
```{r, include=FALSE}

#function to load posture library
#ID to unify posture IDs across annotations
load_cc <- function(x){
  readRDS(x) %>%
    mutate(annotation=gsub("\\d+_(.+)_cluster_centers_reduced.RDS", "\\1",basename(x))) %>%
    mutate(ID = paste0(newID, "_", annotation))
}

#all posture libraries (aka "cluster centers reduced") have to be in one folder
cc_list <- list.files(target_folder,"_cluster_centers_reduced.RDS", full.names = TRUE)

#load data
cluster_centers_reduced <- cc_list %>%
  map_df(., load_cc)

unique(cluster_centers_reduced$annotation)

```


#clustering of posture libraries across annotations
#this is done by another round of kmeans clustering this time only on posture libraries but across annotations/datasets
#also we now cluster (unified) x/y positions instead of angles, this seems to work better...
```{r, include=FALSE}

plot_posture_examples <- function(data_to_plot,X,Y){
  ggplot(data_to_plot, aes_string(x=X,y=Y,color="angle"))+
    geom_point(size=3.5) +
    geom_path(size=2.5,lineend = "round") +
    theme_void()+
    coord_fixed(ratio = 1)+
    scale_color_gradient2(low = "deepskyblue", mid = "lavender",
                          high = "deeppink",midpoint=0,limits=c(-1,1),na.value="grey") +
    # scale_color_viridis(option = "plasma",limits=c(-1,1))+
    theme(plot.title = element_text(face = "bold"))
}


#create specific folder location that will be used to save the heatmaps
save_path <- file.path(base_path,"plots","posture","posture_groups")
dir.create(save_path)

#data frame, every column is an x or y position for each segment of the posture (newID)
ccr_for_clustering <- filter(cluster_centers_reduced,newID_sub == 1) %>%
  select(ID,index,X,Y) %>%
  pivot_wider(names_from = index, values_from = c(X,Y)) %>%
  # mutate(newID = paste0("posture_", newID)) %>%
  column_to_rownames(var = "ID")

#the functions below perform the "elbow plot" for finding the right number of k clusters
# # function to compute total within-cluster sum of square
# wss <- function(k) {
#   kmeans(ccr_for_clustering, k)$tot.withinss
# }
# 
# # Compute and plot wss for k = 1 to k = 15
# k.values <- 1:15
# 
# # extract wss for 2-15 clusters
# wss_values <- map_dbl(k.values, wss)
# 
# plot(k.values, wss_values,
#        type="b", pch = 19, frame = FALSE,
#        xlab="Number of clusters K",
#        ylab="Total within-clusters sum of squares")

#kmeans clustering is performed here
k_ccr <- kmeans(ccr_for_clustering, 6)

#new dataframe that contains the ID (posture ID (newID) combined with annotatation) and the new posture group the new ID belongs to(after clustering)
postures_grouped <- data.frame(posture_grouped= as.character(k_ccr$cluster), ID = rownames(ccr_for_clustering),stringsAsFactors = FALSE)

#bring together original posture library with new posture group
cluster_centers_reduced_grouped <- left_join(cluster_centers_reduced, postures_grouped, by="ID") %>%
  filter(newID_sub == 1) %>%
  mutate(posture_grouped = paste0("group_",posture_grouped)) %>%
  select(annotation,newID,index,X,Y,angle, posture_grouped)

#plot overview seperately for each posture group (across annotations)
for (i in seq(1,6)){
data_to_plot <- cluster_centers_reduced_grouped %>%
    filter(posture_grouped == paste0("group_",i))
number_of_IDs <- length(unique(data_to_plot$newID))
plot_posture_examples(data_to_plot, "X","Y") +
  geom_point(data=filter(data_to_plot,index == 2), aes(X,Y),color="orange",size=7,shape=17) +
  facet_wrap(vars(posture_grouped,newID,annotation),ncol=sqrt(number_of_IDs)) +
  theme(strip.text.x = element_text(size = 20,face="bold"))+
  ggsave(file.path(save_path,paste0("group_",i,".png")),height=sqrt(number_of_IDs)*5,width=30,limitsize=FALSE)
}

```

#Load data for quantifying posture group occurences (this is the angle_data_postures_per_dataset from "plot_postures.Rmd")
```{r, include=FALSE}

#function to load posture library
#ID to unify posture IDs across annotations
load_cc <- function(x){
  readRDS(x)
}

#all posture libraries (aka "cluster centers reduced") have to be in one folder
cc_list <- list.files(target_folder,"_angle_data_postures_per_dataset.RDS", full.names = TRUE)
cc_list

#load data
angle_data_postures_per_dataset <- cc_list %>%
  map_df(., load_cc) %>%
  mutate(ID = paste0(newID, "_", annotation)) %>%
  left_join(postures_grouped, by="ID") %>%
  select(-ID)

unique(angle_data_postures_per_dataset$annotation)
```

#calculate relative occurence of posture groups
```{r, include=FALSE}

postures_grouped_statistics <- angle_data_postures_per_dataset %>%
  #do this seperately for each annotation, dataset, timepoint (hours_rounded) and posture group
  group_by(annotation,dataset_ID, hours_rounded,posture_grouped) %>%
  #How often members of one posture group (adding all number of cluster members per tp per dataset within this group)
  mutate(number_of_posture_members_per_tp_per_dataset = sum(number_of_cluster_members_per_tp_per_dataset)) %>%
  #Normalize this with the numbers of postures per tp per tp 
  mutate(perc_per_posture_grouped_per_dataset = number_of_posture_members_per_tp_per_dataset/postures_per_tp_per_dataset) %>%
  #the rest is done across time (z-score calculation)
  group_by(dataset_ID, posture_grouped) %>%
  mutate(sd_perc_per_posture_grouped_per_dataset = sd(perc_per_posture_grouped_per_dataset)) %>%
  mutate(mean_perc_per_posture_grouped_per_dataset = mean(perc_per_posture_grouped_per_dataset)) %>%
  mutate(perc_norm_per_posture_grouped_per_dataset =  (perc_per_posture_grouped_per_dataset-mean_perc_per_posture_grouped_per_dataset)/sd_perc_per_posture_grouped_per_dataset) %>%
  group_by(annotation, dataset_ID, hours_rounded, posture_grouped,
           perc_per_posture_grouped_per_dataset,
           sd_perc_per_posture_grouped_per_dataset,
           mean_perc_per_posture_grouped_per_dataset,
           perc_norm_per_posture_grouped_per_dataset) %>%
  summarise()
  

unique(postures_grouped_statistics$annotation)
selected_annotation <-unique(postures_grouped_statistics$annotation)

data_for_plotting <- postures_grouped_statistics %>%
  filter(annotation %in% selected_annotation)

ggplot(data_for_plotting, aes(y=perc_norm_per_posture_grouped_per_dataset,x=hours_rounded,color=annotation))+
  geom_point(alpha=0.5)+
  scale_y_continuous(limits = c(-3,3))+
  scale_x_continuous(breaks = c(0,6,12))+
  geom_smooth()+
  theme_minimal()+
        theme(
        strip.background = element_rect(colour = "white", fill = "white"),
        panel.spacing = unit(1, "lines"),
        strip.text.x = element_text(size=15,colour = "black", face = "bold"),
        axis.text.x = element_text(size=30),
        axis.title.x = element_text(size=20),
        axis.text.y = element_text(size=30),
        axis.title.y = element_text(size=20),
        axis.ticks=element_line(size=1.5),
        axis.ticks.length=unit(0.25,"cm"),
        axis.line = element_line(colour = 'black', size = 1.5),
        legend.key.size = unit(2.5, "cm"))+
  facet_wrap(vars(posture_grouped,annotation),ncol=length(selected_annotation),scales="free")+
  ggsave(file.path(save_path,"posture_groups_relative_occurences_norm.png"),height=30,width=25)

ggplot(data_for_plotting, aes(y=perc_per_posture_grouped_per_dataset,x=hours_rounded,color=annotation))+
  geom_point(alpha=0.5)+
  scale_y_continuous(limits = c(0,0.4))+
  scale_x_continuous(breaks = c(0,6,12))+
  geom_smooth()+
  theme_minimal()+
        theme(
        strip.background = element_rect(colour = "white", fill = "white"),
        panel.spacing = unit(1, "lines"),
        strip.text.x = element_text(size=15,colour = "black", face = "bold"),
        axis.text.x = element_text(size=30),
        axis.title.x = element_text(size=20),
        axis.text.y = element_text(size=30),
        axis.title.y = element_text(size=20),
        axis.ticks=element_line(size=1.5),
        axis.ticks.length=unit(0.25,"cm"),
        axis.line = element_line(colour = 'black', size = 1.5),
        legend.key.size = unit(2.5, "cm"))+
  facet_wrap(vars(posture_grouped,annotation),ncol=length(selected_annotation),scales="free")+
  ggsave(file.path(save_path,"posture_groups_relative_occurences.png"),height=30,width=25)


```


#Use after calculating relative occurence of clusters
```{r, include=FALSE}
#define color palette for plots
library(wesanderson)
mr3 <- wes_palettes$Moonrise3[3:2]

save_path <- file.path(base_path,"plots","posture","boxplots_posture_freqs")
dir.create(save_path)


#new function to plot posture examples
plot_posture_examples <- function(data_to_plot,X,Y){
  ggplot(data_to_plot, aes_string(x=X,y=Y,color="angle"))+
    geom_point(size=4) +
    geom_path(size=2,lineend = "round") +
    theme_void()+
    coord_fixed(ratio = 1)+
    #add some buffer on y axis to show full skeleton
    scale_y_continuous(limits=c(0,1.1))+
    scale_color_gradient2(low = "deepskyblue", mid = "lavender",
                          high = "deeppink",midpoint=0,limits=c(-1,1),na.value="grey") +
    # scale_color_viridis(option = "plasma",limits=c(-1,1))+
    theme(plot.title = element_text(face = "bold"))
}
#get names of all newIDs
all_IDs <- unique(cluster_centers_reduced$newID)

#for every cluster ID, calculate wilcoxon rank test pvalue between time bins and append to one matrix
all_ps <- NULL
for (i in all_IDs) {
  p <- angle_data_postures_per_dataset %>%
    #only one clusterID
    filter(newID == i) %>%
    #only for timepoints lower than 6 hours
    filter(hours_rounded <= 6) %>%
    #create time bins
    mutate(time_bin = ifelse(hours_rounded <= 3, "< 3","> 3")) %>%
    #calculate pvalue for only annotation
    filter(annotation == "N2 RT no food") %>%
    select(perc_per_dataset,time_bin) %>%
    #use the perc_per_dataset for calculation
    summarise(Wilcox = wilcox.test(perc_per_dataset~time_bin, data=., paired=FALSE)$p.value) %>%
    mutate(newID = i) %>%
    mutate(Wilcox = as.numeric(Wilcox))
  
  all_ps <- rbind(all_ps, p)
}

all_ps %>%
  arrange(Wilcox) %>%
  slice(1:30)

#take the clusterIDs with the lowest pvalue
significant_IDs <- all_ps %>%
  arrange(Wilcox) %>%
  slice(1:30) %>%
  pull(newID)

#for all IDs plot boxplot and corresponding plosture
for (i in all_IDs){
  
  pvalue <- all_ps %>%
    filter(newID == i) %>%
    select(Wilcox) %>%
    pull()
  
  data_to_plot <- angle_data_postures_per_dataset %>%
    filter(newID %in% i) %>%
    #only for timepoints lower than 6 hours
    filter(hours_rounded <= 6) %>%
    mutate(time_bin = ifelse(hours_rounded <= 3, "< 3h","> 3h")) %>%
    #frequency * 1000
    mutate(perc_per_dataset = perc_per_dataset * 1000)
  
  data_to_plot$annotation <- factor(data_to_plot$annotation, levels=rev(unique(data_to_plot$annotation)))
  
  boxplots <- ggplot(data_to_plot, aes(x=time_bin, y=perc_per_dataset))+
   geom_boxplot(aes(fill=annotation),lwd=1.2,outlier.shape=NA)+
   geom_point(aes(fill=annotation),position = position_jitterdodge(),shape=21,size=2.5)+
   xlab("hours") + ylab("frequency / 1000")+
    scale_fill_manual(values=mr3)+
    theme_classic()+
    theme(
      legend.direction="vertical",
      legend.position = "right",
      strip.background = element_rect(colour = "white", fill = "white"),
      panel.spacing = unit(1, "lines"),
      strip.text.x = element_text(size=15,colour = "black", face = "bold"),
      axis.text.x = element_text(size=30),
      axis.title.x = element_text(size=20),
      axis.text.y = element_text(size=30),
      axis.title.y = element_text(size=20),
      axis.ticks=element_line(size=1.5),
      axis.ticks.length=unit(0.25,"cm"),
      axis.line = element_line(colour = 'black', size = 1.5),
      legend.key.size = unit(2.5, "cm"))
  
  skeletons <- plot_posture_examples(filter(cluster_centers_reduced,newID %in% i & newID_sub == 1), "X","Y") +
    geom_point(data=filter(cluster_centers_reduced,index == 2 & newID == i & newID_sub == 1), aes(X,Y),color="orange",size=5,shape=17)+
    ggtitle(paste0("posture_",i,"\npvalue= ",round(pvalue,10)))
  
  boxplots + skeletons +
    plot_layout(heights = unit(c(5, 1), c('cm', 'null')))+
    ggsave(file.path(save_path,paste0("boxplot_freq_posture_",i,".png")),width=7,height=5)
  
}


```