---
title: "headseq_analysis_deseq2_1"
author: "Friedrich Preußer"
date: "7/26/2021"
output: html_document
---

```{r, results='hide',message='false', warning='false'}
# for all good stuff
library(tidyverse)
# for file manipulation
library(here)
#for labels in plots
library(ggrepel)
#for color
library(wesanderson)
#for other colors
library(RColorBrewer)
#for differential gene expression
library(DESeq2)
#for venn diagram
library(ggvenn)
#for converting gene IDs and goterm analysis
library(gprofiler2)
#for handy plotting of heatmaps
library(pheatmap)
#for LFC estimation
library(apeglm)
library(ashr)

```

#functions
```{r echo=TRUE}

pal <- wes_palette("Darjeeling1")[c(5,1)]

#this function can results in NAs
to_ENSEMBL_name <- function(input){
  gconvert(input,
      organism = "celegans",
      target = "ENSG",
      numeric_ns = "",
      #show only one result
      mthreshold = 1,
      filter_na = FALSE
    )$name
}

``` 

# import data
```{r echo=TRUE, message=FALSE, warning=FALSE}

data <- readRDS(list.files(here("csvs"),"RDS",full.names = TRUE)) %>%
  mutate(exp_condition=gsub("(.+\\_.+)\\_.+","\\1",name))


expressed_genes_head <- read_csv("expressed_genes_head_all_exps.txt") %>% pull()
```


# creating the Deseq2 object
## here we only look at head samples (0h, 3h, 6h, 9h)
#### deseq2 normalizes for 2 things: library size but also library composition.
#### gene counts are LOGe transformed (geometric average) across samples on a per gene basis.
#### genes with value 0 are filtered out.
#### subtract the average log value from the log count across genes
#### now per sample: median of all gene ratios log(counts/average counts across samples)

```{r echo=TRUE, message=FALSE, warning=FALSE}

for_deseq <- data %>%
  #exclude timepoint 0
  filter(tp %in% c("0h","3h","6h","9h")) %>%
  #exclude genes with low readcounts
  # filter(count > 10) %>%
  #here we select wb_gene since this gives unique gene names
  select(gene,exp,condition,tp,count) %>%
  pivot_wider(names_from = c(exp,condition,tp), values_from = count) %>%
  tibble::column_to_rownames(var = "gene")
  

# #discard genes that are not present in all experiments
# for_deseq_clean <- for_deseq %>%
#   na.omit()

# set genes that are not present in all experiments to 0
for_deseq_clean <- for_deseq %>%
  replace(is.na(.), 0)



#create design file
cols <- gsub("FP.+\\_(.+\\_.+)$","\\1" ,colnames(for_deseq_clean))
coldata <- cols %>%
  as.data.frame() %>%
  mutate(condition_tp=gsub(".+\\_(.+^)","\\1",.)) %>%
  select(!.)

rownames(coldata) <- colnames(for_deseq_clean)



dds <- DESeqDataSetFromMatrix(countData = for_deseq_clean,
                              colData = coldata,
                              design = ~  condition_tp)
dds <- DESeq(dds)
```


# differential gene expression with DeSeq2
## here we compare different conditions and timepoints
### we also filter to have a conservative estimate: only log2fold change of > 1 (two-fold change) and padj < 0.05
```{r echo=TRUE, message=FALSE, warning=FALSE}

#---------
tp1 <- "0h"
tp2 <- "3h"
#---------

A_tp1 <- paste0("A_",tp1) 
A_tp2 <- paste0("A_",tp2) 
B_tp1 <- paste0("B_",tp1) 
B_tp2 <- paste0("B_",tp2) 


#we create a seperate deseq2 object with only the samples we want to compare
#create design file
cols <- gsub("FP.+\\_(.+\\_.+)$","\\1" ,colnames(for_deseq_clean))

#extract condition and timepoint as new variable "condition_tp"
coldata <- cols %>%
  as.data.frame() %>%
  mutate(condition_tp=gsub(".+\\_(.+^)","\\1",.)) %>%
  select(!.)

#
rownames(coldata) <- colnames(for_deseq_clean)



#compute the contrast for between different conditions within the same timepoint 
#within the contrast argument the 3rd value is the reference (i.e. control) to compare to.
de_results_B <- lfcShrink(dds, contrast = c("condition_tp", B_tp2, B_tp1), type="ashr")
de_results_A <- lfcShrink(dds, contrast = c("condition_tp", A_tp2,  A_tp1),type="ashr")


de_results_A_df <- de_results_A %>%
  as.data.frame() %>%
  rownames_to_column("gene")

de_results_B_df <- de_results_B %>%
  as.data.frame() %>%
  rownames_to_column("gene")

de_results_A_filtered <- de_results_A_df %>%
  arrange(padj) %>%
  filter(padj < 0.05) %>%
  filter(log2FoldChange > 1 | log2FoldChange < -1) %>%
  mutate(compared_condition = "A") %>%
  mutate(gene_wb = gene) %>%
  mutate(gene = to_ENSEMBL_name(gene))

de_results_B_filtered <- de_results_B_df %>%
  arrange(padj) %>%
  filter(padj < 0.05) %>%
  filter(log2FoldChange > 1 | log2FoldChange < -1) %>%
  mutate(compared_condition = "B") %>%
  mutate(gene_wb = gene) %>%
  mutate(gene = to_ENSEMBL_name(gene))



# list of genes that are specific for condition A
de_results_filtered_merged_for_A <- de_results_B_filtered %>%
  #rows in de_results_A that have no match will have NA values
  right_join(de_results_A_filtered,by="gene",suffix=c("_B","_A")) %>%
  # by selecting those with NA values we select genes "exclusive" for A condition
  filter(is.na(padj_B)) %>%
  # keep only relevant columns
  select(!c(matches("_B"))) %>%
  #clean column names
  rename_with(~ gsub('(.+)\\_A', '\\1', .x))

  
# list of genes that are specific for condition B
de_results_filtered_merged_for_B <- de_results_A_filtered %>%
  #rows in de_results_B that have no match will have NA values
  right_join(de_results_B_filtered,by="gene",suffix=c("_A","_B")) %>%
  #by selecting those with NA values (here in the padj_A) we select genes "exclusive" for B condition
  filter(is.na(padj_A)) %>%
  #keep only relevant columns
  select(!c(matches("_A"))) %>%
  #clean column names
  rename_with(~ gsub('(.+)\\_B', '\\1', .x))

# list of genes that are differentially expressed in both conditions
de_results_filtered_merged_in_both <- de_results_A_filtered %>%
  #rows in de_results_B that have no match will have NA values
  inner_join(de_results_B_filtered,by="gene",suffix=c("_A","_B")) %>%
  dplyr::rename(gene_wb=gene_wb_A) %>%
  select(!gene_wb_B)

write_csv(de_results_filtered_merged_for_A, paste0("diff_specific_for_A_",tp1,"_vs_",tp2,".txt"))
write_csv(de_results_filtered_merged_for_B, paste0("diff_specific_for_B_",tp1,"_vs_",tp2,".txt"))
write_csv(de_results_filtered_merged_in_both, paste0("diff_in_both_",tp1,"_vs_",tp2,".txt"))

```


# overlap differentially expressed genes (across conditions) between timepoints
```{r echo=TRUE, message=FALSE, warning=FALSE}
  
  x <- list(
    A=de_results_A_filtered$gene_wb,
    B=de_results_B_filtered$gene_wb
  )
  
  ggvenn(
    x, 
    fill_color = pal,
    show_outside = "none",
    fill_alpha = 1,
    auto_scale=TRUE,
    show_percentage = FALSE,
    text_size = 0
    
    )
  ggsave(file.path(here(),paste0(tp1,"_vs_",tp2,"_vennDiagram.png")))
  
  
```

```{r echo=TRUE, message=FALSE, warning=FALSE}

#specific for A, B, or both?
#if "both" is selected than volcano plot will show all genes (with associated log2fc and padj) from "A"


plot_volcano <- function(specific_for, what_to_highlight, v){
  
  if(specific_for == "A"){
    df <- de_results_A_df
    dff <- de_results_filtered_merged_for_A
    
  }else if(specific_for == "B"){
    df <- de_results_B_df
    dff <- de_results_filtered_merged_for_B

  }else if(specific_for == "both"){
    dff <- de_results_filtered_merged_in_both %>%
      select(c(matches("_A"),"gene","gene_wb")) %>%
      #clean column names
      rename_with(~ gsub('(.+)\\_A', '\\1', .x))
    df <- dff

  }


  if(what_to_highlight == "gene"){
    ex_genes_highlighted <- dff %>%
      mutate(gene=to_ENSEMBL_name(gene_wb)) %>%
      filter(grepl(v, gene)) %>%
      # filter(-log10(padj) > 5) %>%
      pull(gene_wb)
    
    ex_genes_labeled <- ex_genes_highlighted
    
  }else if(what_to_highlight == "padj"){
    ex_genes_highlighted <- dff %>%
      filter(padj < v) %>%
      pull(gene_wb)
      
    ex_genes_labeled <- dff %>%
      filter(padj < v) %>%
      filter(padj < 10^-2.5) %>%
      pull(gene_wb)
  }

  df_highlighted <- df %>%
    mutate(highlight=ifelse(gene_wb %in% ex_genes_highlighted, gene_wb, NA)) %>%
    mutate(to_be_labeled=ifelse(gene_wb %in% ex_genes_labeled, gene, NA)) %>%
    mutate(labeled=to_ENSEMBL_name(to_be_labeled)) %>%
    mutate(labeled=ifelse(is.na(labeled), to_be_labeled,labeled)) %>%
    select(!to_be_labeled)
  
  
  ggplot(df_highlighted,aes(log2FoldChange,-log10(padj),label = labeled))+
    geom_point(alpha=0.25,fill="lightblue",shape=21)+
    geom_point(data=df_highlighted %>% filter(highlight %in% ex_genes_highlighted),aes(log2FoldChange,-log10(padj)),fill="orange",shape=21)+
    geom_text_repel(
      size=3,
      nudge_x = .15,
      box.padding = 0.05,
      nudge_y = 1,
      segment.curvature = -0.1,
      segment.ncp = 3,
      segment.angle = 20
    )+
    geom_hline(yintercept=-log10(0.05),alpha=0.5,linetype="dashed")+
    geom_vline(xintercept=1,alpha=0.5,linetype="dashed")+
    geom_vline(xintercept=-1,alpha=0.5,linetype="dashed")+
    theme_bw()
  
  ggsave(file.path(here(),paste0("volcano_",tp2,"_vs_",tp1,"_de_specific_for_",specific_for,"_",what_to_highlight,"_",v,".png")),width = 10,height = 10)

}


plot_volcano("both","padj",0.05)
plot_volcano("both","gene","daf-28|ins|nlp|flp")

# plotCounts(dds, gene="T19A6.2", intgroup="condition_tp")

```





# take differentially expressed genes as calculated above (those that are exclusively differentially expressed in one condition)
```{r,results='hide',message='false',warning='false'}

#specific for A, B, or both?
specific_for <- "both"

#get the list of differentially expressed genes of interest
if(specific_for == "A"){
  genesOfInterest <- de_results_filtered_merged_for_A$gene_wb
  tp_one <- paste0("A_",tp1) 
  tp_two <- paste0("A_",tp2)
  tp_three <- "NA"
  tp_four <- "NA"
}else if(specific_for == "B"){
  genesOfInterest <- de_results_filtered_merged_for_B$gene_wb
  tp_one <- paste0("B_",tp1) 
  tp_two <- paste0("B_",tp2)
  tp_three <- "NA"
  tp_four <- "NA"
}else if(specific_for == "both"){
  genesOfInterest <- de_results_filtered_merged_in_both$gene_wb
  tp_one <- paste0("A_",tp1)
  tp_two <- paste0("B_",tp1)
  tp_three <- paste0("A_",tp2)
  tp_four <- paste0("B_",tp2)
}


#calculate enriched GO terms
#against all annotated genes
# goResults <- gost(query = genesOfInterest,
#                 organism = 'celegans',
#                 evcodes = TRUE)

    
#with custom background
goResults <- gost(query = genesOfInterest,
                  organism = 'celegans',
                  evcodes = TRUE,
                  domain_scope="custom",
                  user_threshold = 0.01,
                  custom_bg = expressed_genes_head)


#transform to data frame
go_results <- goResults$result
#sort by pvalue
go_results <- go_results[order(go_results$p_value),]

#plot barplot with enriched GOterms
# only BP == biological process
go_to_plot <- go_results %>%
  top_n(-5,p_value)

ggplot(go_to_plot,aes(-log10(p_value),factor(term_name, levels = rev(term_name))))+
  geom_bar(stat = "identity",color="black",fill="darkgrey")+
  theme_bw()

ggsave(file.path(here(),paste0("enriched_goterms_",tp_one,"_vs_",tp_two,"_and_",tp_three,"_vs_",tp_four,".png")),height = 6,width=12)

```


```{r,results='hide',message='false',warning='false'}

#3h vs 0h
#differentially expressed genes in BOTH conditions
#first term (BP)
# goterm_to_look_for <- "GO:0055114" #obsolete oxidation-reduction process
#second term
# goterm_to_look_for <- "GO:0016491" #oxidoreductase activity
#third term (CC)
# goterm_to_look_for <- "GO:0005777" #peroxisome



#extract goterm name for plot
term_name <- go_results[go_results$term_id == goterm_to_look_for,"term_name"]


#filter out the genes that are part of a particular GO term
geneset_1 <- go_results %>%
  filter(term_id %in% goterm_to_look_for) %>%
  pull() %>%
  strsplit(., ",") %>%
  unlist()

#table get normalized counts from DESeq2 results
normalizedCounts <- DESeq2::counts(dds, normalized = TRUE)
# get the expression data for the gene set of interest
M <- normalizedCounts[rownames(normalizedCounts) %in% geneset_1, ]


#only conditions that we are interested in (for which we did the enrichment analysis)
M <- M %>%
  as.data.frame() %>%
  select(.,matches(tp_one) | matches(tp_two) | matches(tp_three) | matches(tp_four)) %>%
  tibble::rownames_to_column("gene") %>%
  mutate(gene=to_ENSEMBL_name(gene)) %>%
  tibble::column_to_rownames(var = "gene") %>%
  as.matrix()

# log transform the counts for visualization scaling by row helps visualizing
# relative change of expression of a gene in multiple conditions

pheatmap(log2(M+1),
         color=brewer.pal(11,"PiYG"),
         annotation_col = coldata, 
         show_rownames = TRUE,
         # show_colnames = FALSE,
         fontsize_row = 8,
         scale = 'row', 
         cutree_cols = 2, 
         cutree_rows = 2,
         cellheight=6,
         main=paste0(term_name, " (", goterm_to_look_for,")"),
         filename=file.path(here(),paste0("heatmap_specific_for_",tp2,"_vs_",tp1,"_",specific_for,"_",goterm_to_look_for[1],".png")))

```
