---
title: "headseq_analysis_deseq2_1"
author: "Friedrich Preußer"
date: "7/26/2021"
output: html_document
---

```{r, results='hide',message='false', warning='false'}
# for all good stuff
library(tidyverse)
# for file manipulation
library(here)
#for labels in plots
library(ggrepel)
#for color
library(wesanderson)
#for other colors
library(RColorBrewer)
#for differential gene expression
library(DESeq2)
#for venn diagram
library(ggvenn)
#for converting gene IDs and goterm analysis
library(gprofiler2)
#for handy plotting of heatmaps
library(pheatmap)
#for LFC estimation
library(apeglm)
library(ashr)

```

#functions
```{r echo=TRUE}


plot_volcano <- function(what_to_highlight, v){
  
    df <- de_results_df
    dff <- de_results_filtered
    
  if(what_to_highlight == "gene"){
    ex_genes_highlighted <- dff %>%
      filter(grepl(v, gene)) %>%
      # filter(-log10(padj) > 5) %>%
      pull(gene_wb)
    
    ex_genes_labeled <- ex_genes_highlighted
    
  }else if(what_to_highlight == "padj"){
    ex_genes_highlighted <- dff %>%
      filter(padj < v) %>%
      pull(gene_wb)
      
    ex_genes_labeled <- dff %>%
      filter(padj < v) %>%
      filter(padj < 10^-3) %>%
      pull(gene_wb)
  }

  df_highlighted <- df %>%
    mutate(highlight=ifelse(gene_wb %in% ex_genes_highlighted, gene, NA)) %>%
    mutate(to_be_labeled=ifelse(gene_wb %in% ex_genes_labeled, gene, NA)) %>%
    mutate(labeled=to_ENSEMBL_name(to_be_labeled)) %>%
    mutate(labeled=ifelse(is.na(labeled), to_be_labeled,labeled)) %>%
    select(!to_be_labeled)
  
  
  
  ggplot(df_highlighted,aes(log2FoldChange,-log10(padj),label = labeled))+
    geom_point(alpha=0.25,fill="lightblue",shape=21)+
    geom_point(data=df_highlighted %>% filter(gene_wb %in% ex_genes_highlighted),aes(log2FoldChange,-log10(padj)),fill="orange",shape=21)+
    geom_text_repel(
      size=3,
      nudge_x = .15,
      box.padding = 0.05,
      nudge_y = 1,
      segment.curvature = -0.1,
      segment.ncp = 3,
      segment.angle = 20
    )+
    geom_hline(yintercept=-log10(0.05),alpha=0.5,linetype="dashed")+
    geom_vline(xintercept=1,alpha=0.5,linetype="dashed")+
    geom_vline(xintercept=-1,alpha=0.5,linetype="dashed")+
    theme_bw()
  
  ggsave(file.path(here(),paste0("volcano_",A_tp1,"_vs_",B_tp1,"_",what_to_highlight,"_",v,".png")),width = 10,height = 10)

}

plot_counts_ggplot <- function(geneset,selected_tps){
  counts <<- normalizedCounts[rownames(normalizedCounts) %in% geneset, ] %>%
    as.data.frame() %>%
    tibble::rownames_to_column("gene") %>%
    gather(key="name",value=counts_norm,-"gene") %>%
    mutate(exp=gsub("(.+)\\_.+\\_.+","\\1",name)) %>%
    mutate(condition=gsub(".+\\_(.+)\\_.+","\\1",name)) %>%
    mutate(tp=gsub("FP.+\\_.+\\_(.+)h*","\\1",name)) %>%
    filter(tp %in% selected_tps) %>%
    mutate(gene_wb=gene) %>%
    mutate(gene=to_ENSEMBL_name(gene_wb))%>%
    ungroup() %>%
    mutate(counts_norm=ifelse(counts_norm < 1, 1,counts_norm))
  
  ggplot(counts, aes(y=gene,x=log10(counts_norm),fill=condition))+
    geom_boxplot(position=position_dodge(width=0.75),alpha=0,width=0.25)+
    geom_point(position=position_dodge(width=0.75),shape=21,color="black")+
    theme_bw()+
    scale_fill_manual(values = pal)+
    ggtitle(selected_tps)
}

pal <- wes_palette("Darjeeling1")[c(5,1)]

#this function can results in NAs
to_ENSEMBL_name <- function(input){
  gconvert(input,
      organism = "celegans",
      target = "ENSG",
      numeric_ns = "",
      #show only one result
      mthreshold = 1,
      filter_na = FALSE
    )$name
}

``` 

# import data
```{r echo=TRUE, message=FALSE, warning=FALSE}

location_files_to_load <- "/Users/fpreuss/Documents/PhD/Data/headseq/csvs/"
data <- readRDS(list.files(location_files_to_load ,"RDS",full.names = TRUE))

expressed_genes_head <- read_csv("/Users/fpreuss/Documents/PhD/Data/headseq/expressed_genes_head_all_exps.txt") %>% pull()
```


# creating the Deseq2 object
## here we only look at head samples (0h, 3h, 6h, 9h)
#### deseq2 normalizes for 2 things: library size but also library composition.
#### gene counts are LOGe transformed (geometric average) across samples on a per gene basis.
#### genes with value 0 are filtered out.
#### subtract the average log value from the log count across genes
#### now per sample: median of all gene ratios log(counts/average counts across samples)

```{r echo=TRUE, message=FALSE, warning=FALSE}

for_deseq <- data %>%
  #exclude timepoint 0
  filter(tp %in% c("0h","3h","6h","9h")) %>%
  #exclude genes with low readcounts
  # filter(count > 10) %>%
  #here we select wb_gene since this gives unique gene names
  select(gene,exp,condition,tp,count) %>%
  pivot_wider(names_from = c(exp,condition,tp), values_from = count) %>%
  tibble::column_to_rownames(var = "gene")
  

# #discard genes that are not present in all experiments
# for_deseq_clean <- for_deseq %>%
#   na.omit()

# set genes that are not present in all experiments to 0
for_deseq_clean <- for_deseq %>%
  replace(is.na(.), 0)



#create design file
cols <- gsub("FP.+\\_(.+\\_.+)$","\\1" ,colnames(for_deseq_clean))
coldata <- cols %>%
  as.data.frame() %>%
  mutate(condition_tp=gsub(".+\\_(.+^)","\\1",.)) %>%
  select(!.)

rownames(coldata) <- colnames(for_deseq_clean)



dds <- DESeqDataSetFromMatrix(countData = for_deseq_clean,
                              colData = coldata,
                              design = ~  condition_tp)
dds <- DESeq(dds)
```


# differential gene expression with DeSeq2
## here we compare different conditions WITHIN the same timepoint 
### we also filter to have a conservative estimate: only log2fold change of > 1 (two-fold change) and padj < 0.05
```{r echo=TRUE, message=FALSE, warning=FALSE}

#---------
tp1 <- "9h"
#---------

A_tp1 <- paste0("A_",tp1) 
B_tp1 <- paste0("B_",tp1) 



#we create a seperate deseq2 object with only the samples we want to compare
#create design file
cols <- gsub("FP.+\\_(.+\\_.+)$","\\1" ,colnames(for_deseq_clean))

#extract condition and timepoint as new variable "condition_tp"
coldata <- cols %>%
  as.data.frame() %>%
  mutate(condition_tp=gsub(".+\\_(.+^)","\\1",.)) %>%
  select(!.)

#
rownames(coldata) <- colnames(for_deseq_clean)



#compute the contrast for between different conditions within the same timepoint 
#within the contrast argument the 3rd value is the reference (i.e. control) to compare to.
de_results <- lfcShrink(dds, contrast = c("condition_tp", A_tp1, B_tp1), type="ashr")
# de_results <- results(dds, contrast = c("condition_tp", A_tp1, B_tp1))

# de_results
# summary(de_results)

de_results_df <- de_results %>%
  as.data.frame() %>%
  rownames_to_column("gene") %>%
  mutate(gene_wb = gene) %>%
  mutate(gene = to_ENSEMBL_name(gene)) %>%
  mutate(gene=ifelse(is.na(gene), gene_wb,gene))


de_results_filtered <- de_results_df %>%
  arrange(padj) %>%
  filter(padj < 0.05) %>%
  filter(log2FoldChange > 1 | log2FoldChange < -1)



write_csv(de_results_filtered, paste0("diff_",A_tp1,"_vs_",B_tp1,".txt"))

```



```{r echo=TRUE, message=FALSE, warning=FALSE}




plot_volcano("padj",0.05)
plot_volcano("gene","daf-28|ins|nlp|flp")



```





# take differentially expressed genes as calculated above (those that are exclusively differentially expressed in one condition)
```{r,results='hide',message='false',warning='false'}


#get the list of differentially expressed genes of interest
genesOfInterest <- de_results_filtered$gene_wb


#calculate enriched GO terms
#against all annotated genes
# goResults <- gost(query = genesOfInterest,
#                 organism = 'celegans',
#                 evcodes = TRUE)

    
#with custom background
goResults <- gost(query = genesOfInterest,
                  organism = 'celegans',
                  evcodes = TRUE,
                  domain_scope="custom",
                  user_threshold = 0.01,
                  custom_bg = expressed_genes_head)



#transform to data frame
go_results <- goResults$result
#sort by pvalue
go_results <- go_results[order(go_results$p_value),]


#plot barplot with enriched GOterms
go_to_plot <- go_results %>%
  #filter out transfac missannotation
  filter(!term_name == "Transfac") %>%
  top_n(-5,p_value) %>%
  distinct(term_name, .keep_all= TRUE)

ggplot(go_to_plot,aes(-log10(p_value),factor(term_name, levels = rev(term_name))))+
  geom_bar(stat = "identity",color="black",fill="darkgrey")+
  theme_bw()

ggsave(file.path(here(),paste0("enriched_goterms_",A_tp1,"_vs_",B_tp1,".png")),height = 6,width=12)




```



```{r,results='hide',message='false',warning='false'}


#if background model is all genes measured in our head seqs
#3h vs 3h
#only term
# goterm_to_look_for <- "GO:0005576" #extracellular region

#6h vs 6h
#first term
goterm_to_look_for <- "GO:0007218" #neuropeptide signaling pathway
#second
# goterm_to_look_for <- "KEGG:01212" #fatty acid metabolism
#third
# goterm_to_look_for <- "GO:0005576" #extracellular region
#fourth
# goterm_to_look_for <- "KEGG:04146" #peroxisome
#fith
# goterm_to_look_for <- "KEGG:00071"	#fatty acid degradation

#if background model is all annotated c.elegans genes 
#3h vs 3h
#first term 
# goterm_to_look_for <- "GO:0005576" #extracellular region 
#first KEGG term
# goterm_to_look_for <- "KEGG:01100" #metabolic pathways
#no bp termss

#6h vs 6h
#first term
# goterm_to_look_for <- "GO:0005576" #extracellular region
#first bp term
# goterm_to_look_for <- "GO:0007218" #"neuropeptide signaling pathway"
#first KEGG
# goterm_to_look_for <- "KEGG:01100" #metabolic pathways
#first tf
# goterm_to_look_for <- "TF:M07154" #elt-3 targets
#another KEGG
# goterm_to_look_for <- "KEGG:04146" #peroxisome

#9h vs 9h
#first term
# goterm_to_look_for <- "KEGG:01100" #metabolic pathways 
#first bp term
# goterm_to_look_for <- "GO:0006082" #organic acid metabolic process
#thirs bp term
# goterm_to_look_for <- "GO:0007218" #"neuropeptide signaling pathway"

#extract goterm name for plot
term_name <- go_results[go_results$term_id == goterm_to_look_for,"term_name"]


#filter out the genes that are part of a particular GO term
geneset_1 <- go_results %>%
  filter(term_id %in% goterm_to_look_for) %>%
  pull() %>%
  strsplit(., ",") %>%
  unlist()

#table get normalized counts from DESeq2 results
normalizedCounts <- DESeq2::counts(dds, normalized = TRUE)
# get the expression data for the gene set of interest
M <- normalizedCounts[rownames(normalizedCounts) %in% geneset_1, ]


#only conditions that we are interested in (for which we did the enrichment analysis)
M <- M %>%
  as.data.frame() %>%
  select(.,matches(A_tp1) | matches(B_tp1)) %>%
  tibble::rownames_to_column("gene") %>%
  mutate(gene=to_ENSEMBL_name(gene)) %>%
  tibble::column_to_rownames(var = "gene") %>%
  as.matrix()

# log transform the counts for visualization scaling by row helps visualizing
# relative change of expression of a gene in multiple conditions
pheatmap(log2(M+1),
         color=brewer.pal(11,"PiYG"),
         annotation_col = coldata, 
         show_rownames = TRUE,
         # show_colnames = FALSE,
         fontsize_row = 6,
         scale = 'row', 
         cutree_cols = 2, 
         cutree_rows = 2,
         cellheight=11,
         main=paste0(term_name, " (", goterm_to_look_for,")"),
         filename=file.path(here(),paste0("heatmap_",A_tp1,"_vs_",B_tp1,"_",goterm_to_look_for[1],".png")))


# over all timepoints
counts <- normalizedCounts[rownames(normalizedCounts) %in% geneset_1, ] %>%
    as.data.frame() %>%
    tibble::rownames_to_column("gene") %>%
    gather(key="name",value=counts_norm,-"gene") %>%
    mutate(exp=gsub("(.+)\\_.+\\_.+","\\1",name)) %>%
    mutate(condition=gsub(".+\\_(.+)\\_.+","\\1",name)) %>%
    mutate(tp=gsub("FP.+\\_.+\\_(.+)h*","\\1",name)) %>%
    mutate(gene_wb=gene) %>%
    mutate(gene=to_ENSEMBL_name(gene_wb)) %>%
    group_by(condition,tp,gene) %>%
    summarise(counts_norm_mean = mean(counts_norm))


ggplot(counts, aes(x=tp,y=counts_norm_mean, fill=condition,))+
    # geom_boxplot(aes(fill=condition),outlier.size = .75)+
    # geom_violin()+
    geom_path(aes(group=gene))+
    geom_point(size=4,color="black",shape=21)+
    theme_bw()+
    scale_fill_manual(values = pal)+
    ggtitle(term_name)+
    facet_wrap(vars(condition))
ggsave(file.path(here(), paste0("counts_",A_tp1,"_vs_",B_tp1,"_",goterm_to_look_for[1],"all_timepoints.png")))


# dots for one timepoint
plot_counts_ggplot(geneset_1,c(tp1))
ggsave(file.path(here(), paste0("counts_",A_tp1,"_vs_",B_tp1,"_",goterm_to_look_for[1],".png")))


```

# plot heatmap for a manually defined geneset
```{r echo=TRUE, message=FALSE, warning=FALSE}

pattern <- "^ins\\-*"
geneset_2 <- de_results_filtered[grep(pattern,de_results_filtered$gene),"gene_wb"]


#table get normalized counts from DESeq2 results
normalizedCounts <- DESeq2::counts(dds, normalized = TRUE)
# get the expression data for the gene set of interest
M <- normalizedCounts[rownames(normalizedCounts) %in% geneset_2, ]


#only conditions that we are interested in (for which we did the enrichment analysis)
M <- M %>%
  as.data.frame() %>%
  select(.,matches(A_tp1) | matches(B_tp1)) %>%
  tibble::rownames_to_column("gene") %>%
  mutate(gene=to_ENSEMBL_name(gene)) %>%
  tibble::column_to_rownames(var = "gene") %>%
  as.matrix()

# log transform the counts for visualization scaling by row helps visualizing
# relative change of expression of a gene in multiple conditions

pheatmap(log2(M+1),
         color=brewer.pal(11,"PiYG"),
         annotation_col = coldata, 
         show_rownames = TRUE,
         # show_colnames = FALSE,
         fontsize_row = 8,
         scale = 'row', 
         cutree_cols = 2, 
         cutree_rows = 2,
         cellheight=11,
         main=pattern,
         filename=file.path(here(),paste0("heatmap_",A_tp1,"_vs_",B_tp1,"_",pattern,".png")))


plot_counts_ggplot(geneset_2,c(tp1))
ggsave(file.path(here(), paste0("counts_",A_tp1,"_vs_",B_tp1,"_",pattern,".png")),height=4, width=5)


```


#plot single genes across conditions and timepoints
```{r echo=TRUE, message=FALSE, warning=FALSE}
pattern <- ".*daf-28.*"
#table get normalized counts from DESeq2 results
nc_df <- DESeq2::counts(dds, normalized = TRUE) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("gene") %>%
  mutate(gene_wb = gene) %>%
  mutate(gene = to_ENSEMBL_name(gene)) %>%
  mutate(gene=ifelse(is.na(gene), gene_wb,gene))

selected_gene <- nc_df[grep(pattern,nc_df$gene),"gene_wb"]
 
normalizedCounts <- DESeq2::counts(dds, normalized = TRUE)

counts <- normalizedCounts[rownames(normalizedCounts) %in% selected_gene, ] %>%
  as.data.frame() %>%
  rename(.="counts_norm") %>%
  tibble::rownames_to_column("name") %>%
  mutate(exp=gsub("(.+)\\_.+\\_.+","\\1",name)) %>%
  mutate(condition=gsub(".+\\_(.+)\\_.+","\\1",name)) %>%
  mutate(tp=gsub("FP.+\\_.+\\_(.+)h*","\\1",name)) %>%
  mutate(condition_tp=gsub("FP.+\\_(.+\\_)h*","\\1",name)) %>%
  group_by(condition_tp,condition,tp) %>%
  mutate(mean_counts_norm = mean(counts_norm)) %>%
  mutate(sd_mean_counts_norm = sd(counts_norm))

  

ggplot(data=counts,aes(x=tp,y=counts_norm))+
  geom_pointrange(data=counts, aes(x=tp,y=mean_counts_norm,ymin=mean_counts_norm-sd_mean_counts_norm, ymax=mean_counts_norm+sd_mean_counts_norm,group=condition_tp), width=.1,size=1,position=position_dodge(0.3),shape=3)+
  geom_point(aes(fill=condition),position=position_dodge(0.3),size=5,color="black",shape=21,alpha=0.75)+
  scale_y_continuous(limits=c(0,max(counts$counts_norm)*1.2))+
  theme_bw()+
  scale_fill_manual(values = pal)+
  ggtitle(to_ENSEMBL_name(selected_gene))

  
ggsave(file.path(here(), paste0("genecounts_",to_ENSEMBL_name(selected_gene),".png")))

```
