---
title: "headseq_analysis_deseq2_1"
author: "Friedrich Preußer"
date: "7/26/2021"
output: html_document
---

```{r, results='hide',message='false', warning='false'}
# for all good stuff
library(tidyverse)
# for file manipulation
library(here)
#for labels in plots
library(ggrepel)
#for color
library(wesanderson)
#for differential gene expression
library(DESeq2)
#for venn diagram
library(ggvenn)
#for converting gene IDs and goterm analysis
library(gprofiler2)
#for handy plotting of heatmaps
library(pheatmap)

```

#functions
```{r echo=TRUE}

pal <- wes_palette("Darjeeling1")[c(5,1)]

to_ENSEMBL_name <- function(input){
  gconvert(input,
      organism = "celegans",
      target = "ENSG",
      numeric_ns = "",
      #show only one result
      mthreshold = 1,
      filter_na = FALSE
    )$name
}

``` 

# import data
```{r echo=TRUE, message=FALSE, warning=FALSE}

data <- readRDS(list.files(here("csvs"),"RDS",full.names = TRUE))

```


# creating the Deseq2 object
## here we only look at head samples (0h,3h, 6h, 9h)
#### deseq2 normalizes for 2 things: library size but also library composition.
#### gene counts are LOGe transformed (geometric average) across samples on a per gene basis.
#### genes with value 0 are filtered out.
#### subtract the average log value from the log count across genes
#### now per sample: median of all gene ratios log(counts/average counts across samples)

```{r echo=TRUE, message=FALSE, warning=FALSE}

for_deseq <- data %>%
  #exclude timepoint 0
  filter(tp %in% c("0h","3h","6h","9h")) %>%
  #exclude genes with low readcounts
  # filter(count > 10) %>%
  #here we select wb_gene since this gives unique gene names
  select(gene,exp,condition,tp,count) %>%
  pivot_wider(names_from = c(exp,condition,tp), values_from = count) %>%
  tibble::column_to_rownames(var = "gene")

#set genes that are not present in all experiments to 0
for_deseq_clean <- for_deseq %>%
  replace(is.na(.), 0)

#create design file
cols <- gsub("FP.+\\_(.+\\_.+)$","\\1" ,colnames(for_deseq_clean))
coldata <- cols %>%
  as.data.frame() %>%
  mutate(condition_tp=gsub(".+\\_(.+^)","\\1",.)) %>%
  select(!.)

rownames(coldata) <- colnames(for_deseq_clean)



dds <- DESeqDataSetFromMatrix(countData = for_deseq_clean,
                              colData = coldata,
                              design = ~  condition_tp)
dds <- DESeq(dds)

```

#PCA on normalized counts
```{r echo=TRUE, message=FALSE, warning=FALSE}
number_of_variable_genes <- 500

#PCA (on normalized and log transformed counts, top 500 variable genes)
rld <- rlog(dds)
pca <- DESeq2::plotPCA(rld, ntop = number_of_variable_genes, intgroup = 'condition_tp',returnData=TRUE)

DESeq2::plotPCA(rld, ntop = number_of_variable_genes, intgroup = 'condition_tp')


pca %>%
  mutate(tp=gsub(".*\\_(.*)h","\\1",group)) %>%
  mutate(condition=gsub("(.*)\\_.*","\\1",group)) %>%
  mutate(exp=gsub("(.*)\\_.*\\_.*","\\1",name)) %>%
  mutate(exp_condition=gsub("(.+)\\_.*","\\1",name)) %>%
  mutate(condition=ifelse(condition == "A", "with_food","no_food")) %>%
  ggplot(., aes(PC1,PC2))+
    geom_path(aes(group=exp_condition),alpha=0.25)+
    geom_point(aes(shape=tp, fill=condition),size=3)+
    # ylim(limits=c(-30,40))+
    # xlim(limits=c(-50,60))+
    scale_fill_manual(values=pal[2:1])+
    scale_shape_manual(values=c(21,22,24,23)) + 
    ggtitle(paste0(number_of_variable_genes, " most variable genes as input."))+
    # geom_label_repel(fill = "white", xlim = c(-Inf, Inf), ylim = c(-Inf, Inf))+
    theme_bw()

# ggsave(file.path(here(),paste0("headseq_PCA_",number_of_variable_genes,"_most_variable_genes",".png")))


# 
# #this is code taken out of the DESeq2::plotPCA function
# rv <- rowVars(assay(rld))
# # select the ntop genes by variance
# select <- order(rv, decreasing=TRUE)[seq_len(min(number_of_variable_genes, length(rv)))]
# pca <- prcomp(t(assay(rld)[select,]))
# 
# pca$x %>%
#   as.data.frame() %>%
#   tibble::rownames_to_column("name") %>%
#   mutate(tp=gsub(".*\\_(.*)h","\\1",name)) %>%
#   mutate(condition=gsub(".*\\_(.*)\\_.*","\\1",name)) %>%
#   mutate(exp=gsub("(.*)\\_.*\\_.*","\\1",name)) %>%
#   mutate(exp_condition=gsub("(.+)\\_.*","\\1",name)) %>%
#   mutate(condition=ifelse(condition == "A", "with_food","no_food")) %>%
#   ggplot(., aes(PC1,PC2))+
#     geom_path(aes(group=exp_condition),alpha=0.25)+
#     geom_point(aes(shape=tp, fill=condition),size=3)+
#     # ylim(limits=c(-30,40))+
#     # xlim(limits=c(-50,60))+
#     scale_fill_manual(values=pal[2:1])+
#     scale_shape_manual(values=c(21,22,24,23)) +
#     ggtitle(paste0(number_of_variable_genes, " most variable genes as input."))+
#     # geom_label_repel(fill = "white", xlim = c(-Inf, Inf), ylim = c(-Inf, Inf))+
#     theme_bw()
# 
# 
# loadings <- data.frame(pca$rotation)
# 
# top_loadings_PC1 <- loadings %>%
#   select(PC1) %>%
#   tibble::rownames_to_column("gene_wb") %>%
#   rename(PC1="value") %>%
#   mutate(value_abs=abs(value)) %>%
#   arrange(desc(value_abs)) %>%
#   mutate(gene=to_ENSEMBL_name(gene_wb))
# 
# top_loadings_PC2 <- loadings %>%
#   select(PC2) %>%
#   tibble::rownames_to_column("gene_wb") %>%
#   rename(PC2="value") %>%
#   mutate(value_abs=abs(value)) %>%
#   arrange(desc(value_abs)) %>%
#   mutate(gene=to_ENSEMBL_name(gene_wb))

```


#further quality control
```{r echo=TRUE, message=FALSE, warning=FALSE}


#MA plot
DESeq2::plotMA(object = dds, ylim = c(-5, 5))


#plot to compare raw and normalized count variance
library(EDASeq)

plotRLE(as.matrix(for_deseq_clean), outline=FALSE, ylim=c(-4, 4),
        col=as.numeric(coldata$condition_tp),
        main = 'Raw Counts')

plotRLE(DESeq2::counts(dds, normalized = TRUE),
        outline=FALSE, ylim=c(-4, 4),
        col = as.numeric(coldata$condition_tp),
        main = 'Normalized Counts')
```
